### 2016-01-12 proposal/proposal.tex
initial commit with proposal directory and placeholder tex file for proposal

\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{babel}
\begin{document}

\title{Nass Replication Study}
\author{Matthew Neal, Shaown Sarker}
\maketitle
\end{document}

### 2016-01-20 proposal/proposal.tex
Reviewing previous changes and minor updates

@@
 \usepackage{babel}
+\usepackage{cite}
+\usepackage{url}
+
+% For block comments
+\usepackage{verbatim}
+
+% For paper size and margin manipulation
+\usepackage[a4paper, margin=1in]{geometry}
+
 \begin{document}
 
-\title{Nass Replication Study}
+\title{Project Proposal: Evaluating Politeness toward Computers}
 \author{Matthew Neal, Shaown Sarker}
 \maketitle
+
+Clifford Nass and colleagues' 1999 study on human computer interaction looked to determine whether humans treat computers with politeness or not~\cite{nass1999}.
+Nass found that the social normative bias towards the human interviewer also extended to a computer program based interviewer, although objectively interviewees should not have had such a bias towards a non-human interviewer.
+The explanation of this behavior was that humans do not differentiate between computers and people when it comes to social interactions, and that the normative bias towards a human interviewer also extends to a computer one.
+
+One of the implications found by Nass was that humans simply reuse the same mental construct without much cognitive effort for social interactions with computers instead of forming a new one.
+However, in the intervening 16 years since the study, the sheer number of people with computer access, both at home and workplace, in the US has increased by a significant degree.
+Census reports indicate around 51\% of households had a computer at home in 1999~\cite{newburger2001}, while that percentage had increased to 83\% by 2013~\cite{file2014}.
+Furthermore, smart-phones have become completely ubiquitous over the same time period, the census bureau indicates that 63\% of households had a "handheld computer"(smart-phone, or other wireless computer) in 2013~\cite{file2014}.
+
+The effect of the availability and extended familiarity of computers on human-computer interactions when it comes to interviewer bias has not been studied in depth.
+It seems fair to conclude that a replication of the study, to determine whether the ingratiation towards the computer interviewer perceived by the participants in the original study is influenced by the degree of knowledge of computers, is a worthwhile endeavor.
+
+\begin{comment}
+Clifford Nass' 1999 study on human computer interaction looked to determine whether humans treated computers with politeness or not\cite{nass1999}.
+The study looked at Stanford University students, since the assumption was that such students had access and familiarity with computers and would be assumed to not treat computers in this way.
+Surprisingly Nass' results proved that in fact the students did treat machines with the same sort of politeness what would be accorded to humans.
+
+In the intervening 16 years the sheer number of people with computer access at home in the US has increased by a significant degree.
+Census reports indicate around 51\% of households had a computer at home in 1999\cite{newburger2001}, while that percentage had increased to 83\% by 2013 \cite{file2014}.
+
+Further, smart-phones have become completely ubiquitous over the same time period, the census bureau indicates that 63\% of households had a "handheld computer"(smart-phone, or other wireless computer)\cite{file2014}.
+It seems fair to conclude that a replication of Nass', study in light of the changing relationship that humans have with computers, is a worthwhile endeavour.
+\end{comment}
+
+In this study, we will focus on students from two disciplines within the North Carolina State University community.
+One group will come from Computer Science undergraduate and/or graduate students, and the other will likely be a group of non-Computer Science students.
+The idea with two distinct and separate groups of participants is to have a group of students that are intimately aware of the inner-workings of computer programs and a group of students that are much more likely to have access to computers from a layman rather than expert perspective.
+The underlying goal here is to determine whether the different level of understanding of computer translates differently to the personification that was found by Nass and colleagues back in 1999.
+
+Methodologically we plan to recreate the study in as much detail as possible. Several nuances of this proposed study compared to the original are as follows:
+
+\begin{itemize}
+    \item We intend to use a web-based setup instead of the individual computer based program for the participants, which can be accessed by both their personal computers and/or smart-phones.This way we can have much more flexibility with how we administer the study.
+One possible threat to validity with this change is that if students use their own machines they may well have more of an attachment, for lack of a better word, for that machine which could affect the degree of personification.
+
+    \item In the interview, the participants are presented with a list of random facts, exactly same for all participants and later a quiz based on the facts presented.
+After the participants have completed the quiz, they provide feedback on the tutoring capability of the program via three different means - filling out a feedback form on the same computer, in a paper-pencil form, and on a different computer than the one used to take the quiz.
+In the original study, the tutor program expressed remarks praising itself to elicit positive feedback from the participants, which the authors considered a threat to the validity of their study.
+We will not include any such self-praise to manipulate the feedback of the participants.
+
+    \item The original study contained a part where participants were subject to a voice based program alongside a textual one to emphasize human characteristics of the computer interviewer.
+A voice based study might be out of scope for our study given the time requirements that such a study would require.
+\end{itemize}
+
+At the moment of writing this proposal, our hypothesis is that we will find varying level of personalization between the two groups of participants -- the group with CS background is likely to display more objectivity and thus be less ingratiating to the interviewer program in their feedback compared to the non-CS background group.
+If our hypothesis holds, then it will add to the finding of Nass' and colleagues that the knowledge of underlying workings of computers does indeed effect the social interaction between a human and a computer.
+
+\begin{comment}
+\begin{itemize}
+    \item The Nass study seems to have used some sort of lab setup with computers set aside for this use, we believe we can build a simple website that can be accessed from either mobile or laptop machines rather than have the study take place in a fixed lab.
+This way we can have much more flexibility with how we administer the study.
+The only worry with this change is that if students use their own machines they may well have more of an attachment, for lack of a better word, for that machine.
+    \item Nass' study had the mechanism of using different machines for the survey on the performance of the tutor, we believe that this could end up being at least somewhat troublesome.
+To mitigate that problem we will have students simply use their smartphones to complete the survey rather than the machine that they utilized for the tutoring session.
+    \item We have some concern that building out a voice based version of the same system as was done in Nass' second study may be out of scope for a one semester project, and at least preliminarily assume that the secondary will need to be left out to finish the rest of the study with a reasonable level of quality.
+    \item We are considering building out the tutor aspect of the study as some sort of AI agent using a machine learning algorithm.
+This may simply not be feasible and no attempt will be made to force this into place should it not be workable.
+If we find it infeasible we will simply use the sort of canned responses that are used in the Nass study.
+\end{itemize}
+\end{comment}
+
+\bibliography{cited}{}
+\bibliographystyle{plain}
+
 \end{document}

### 2016-01-21 proposal/proposal.tex
Minor changes to semantics.

@@
 
-One of the implications found by Nass was that humans simply reuse the same mental construct without much cognitive effort for social interactions with computers instead of forming a new one.
+In this study, our primary motivation will be to focus on students from two disciplines within the North Carolina State University community.
+One group will come from Computer Science undergraduate and/or graduate students, and the other will likely be a group of non-Computer Science students.
+The idea with two distinct and separate groups of participants is to have a group of students that are intimately aware of the inner-workings of computer programs and a group of students that are much more likely to have access to computers from a layman rather than expert perspective.
+The underlying goal here is to determine whether the different level of understanding of computers translates differently to the personification that was found by Nass and colleagues back in 1999
+
+In the study, Nass explained that humans simply reuse the same mental construct without much cognitive effort for social interactions with computers instead of forming a new one.
 However, in the intervening 16 years since the study, the sheer number of people with computer access, both at home and workplace, in the US has increased by a significant degree.
@@
 
-The effect of the availability and extended familiarity of computers on human-computer interactions when it comes to interviewer bias has not been studied in depth.
+A secondary motivation for us will be what kind of effect this availability and extended familiarity of computers can have on the interviewer bias, which has not been studied in depth.
 It seems fair to conclude that a replication of the study, to determine whether the ingratiation towards the computer interviewer perceived by the participants in the original study is influenced by the degree of knowledge of computers, is a worthwhile endeavor.
-
-\begin{comment}
-Clifford Nass' 1999 study on human computer interaction looked to determine whether humans treated computers with politeness or not\cite{nass1999}.
-The study looked at Stanford University students, since the assumption was that such students had access and familiarity with computers and would be assumed to not treat computers in this way.
-Surprisingly Nass' results proved that in fact the students did treat machines with the same sort of politeness what would be accorded to humans.
-
-In the intervening 16 years the sheer number of people with computer access at home in the US has increased by a significant degree.
-Census reports indicate around 51\% of households had a computer at home in 1999\cite{newburger2001}, while that percentage had increased to 83\% by 2013 \cite{file2014}.
-
-Further, smart-phones have become completely ubiquitous over the same time period, the census bureau indicates that 63\% of households had a "handheld computer"(smart-phone, or other wireless computer)\cite{file2014}.
-It seems fair to conclude that a replication of Nass', study in light of the changing relationship that humans have with computers, is a worthwhile endeavour.
-\end{comment}
-
-In this study, we will focus on students from two disciplines within the North Carolina State University community.
-One group will come from Computer Science undergraduate and/or graduate students, and the other will likely be a group of non-Computer Science students.
-The idea with two distinct and separate groups of participants is to have a group of students that are intimately aware of the inner-workings of computer programs and a group of students that are much more likely to have access to computers from a layman rather than expert perspective.
-The underlying goal here is to determine whether the different level of understanding of computer translates differently to the personification that was found by Nass and colleagues back in 1999.
+The prevalence of available computers and smart-phones as a major aspect of our study will be impacted by whether or not we are able to obtain the recruitment procedures that Nass used in is original studies.
+If that information is unavailable we will turn all of our attention to our primary motivation.
 
@@
     \item The original study contained a part where participants were subject to a voice based program alongside a textual one to emphasize human characteristics of the computer interviewer.
-A voice based study might be out of scope for our study given the time requirements that such a study would require.
+We believe that a voice based component would be out of scope for our study given the time requirements that such a study would require.
+Additionally, given that Nass' results were similar between the two phases of his study, the assumption is that we are not losing a significant part of the study by decreasing its scope in this way.
 \end{itemize}
@@
 
-\begin{comment}
-\begin{itemize}
-    \item The Nass study seems to have used some sort of lab setup with computers set aside for this use, we believe we can build a simple website that can be accessed from either mobile or laptop machines rather than have the study take place in a fixed lab.
-This way we can have much more flexibility with how we administer the study.
-The only worry with this change is that if students use their own machines they may well have more of an attachment, for lack of a better word, for that machine.
-    \item Nass' study had the mechanism of using different machines for the survey on the performance of the tutor, we believe that this could end up being at least somewhat troublesome.
-To mitigate that problem we will have students simply use their smartphones to complete the survey rather than the machine that they utilized for the tutoring session.
-    \item We have some concern that building out a voice based version of the same system as was done in Nass' second study may be out of scope for a one semester project, and at least preliminarily assume that the secondary will need to be left out to finish the rest of the study with a reasonable level of quality.
-    \item We are considering building out the tutor aspect of the study as some sort of AI agent using a machine learning algorithm.
-This may simply not be feasible and no attempt will be made to force this into place should it not be workable.
-If we find it infeasible we will simply use the sort of canned responses that are used in the Nass study.
-\end{itemize}
-\end{comment}
-
 \bibliography{cited}{}

### 2016-03-14 Final Latex Template/sig-alternate-sample.tex
Updates from ShareLaTeX

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Do Software Developers Love Their Computers More Than Most?}
\subtitle{A Nass Replication}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{6} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{trovato@corporation.com}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file. A compiled PDF version
is available on the web page to help you with the
`look and feel'.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{ACM proceedings; \LaTeX; text tagging}

\section{Introduction}

\section{Related Work}
In research interviews open, frank speech is essential to the process. Interviews are plagued by biases inherent in social interactions. Such biases include the normative-response bias (people not wanting to admit to answers that are counter to the perceived norm), interviewer-based bias (people answering based on the perceived preference of the interviewer), and politeness norms (people modifying answers to avoid offending). Computer systems were introduced to mitigate these known social-biases by providing anonymity. However, through a series of studies, Nass et al. documented how individuals anthropomorphize technology and exhibit attitudes previously thought to be reserved for person to person interaction \cite{nass1999people}\cite{reeves1996people}. Contrary to what was believed at the time, the results suggested that humans unintentionally, unknowingly apply social rules to computer systems.   
This foundational work sparked further studies to replicate, validate, and extend this assertion. Since the initial set of studies were conducted entirely in the United States, additional research validated the findings across other cultures \cite{katagiri2001cross}. Furthermore, the existence of computers as social entities has been studied to better understand racial biases in interviews\cite{krysan2003race}, how the quality of interaction affects expressive systems \cite{vidyarthi2011sympathetic}, and even how to leverage social cues to more effectively sell products online \cite{wang2007can}. To our knowledge, no studies currently exist which attempt to replicate these effects with software developers.   
In order to create better software, it is important to study the attitudes of software developers and how they view their work environments. Given software developers’ advanced understanding of how computers work, one would expect the attribution of social qualities to computers to be minimal or not present. At the same time, it has been shown that humans with accurate mental models are more effective in maintaining teammate bonds with automated computer systems \cite{wilkison2008effects}. Given this premise, we are interested in exploring the following questions:

\begin{itemize}
    \item Do software developers exhibit social-biases towards computers?
    \item Does ownership1 of the computer modify the exhibited social-biases? 
\end{itemize}
%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%
% That's all folks!
\end{document}

### 2016-03-19 Final Latex Template/blob.tex

On the difficulty of replicating human experiments

Exact replications of human experiments are incredibly difficult to perform, because a lot of information is tacit and will not be found in written materials.  Contact with the original authors is almost always necessary.  Differences will inevitably occur, and should be accounted for individually so that results can be directly compared with the original experiment.  Replications should be done to strengthen the original findings or to find biases or errors in the original experiment that can be improved upon.

How people treat computers, television, and new media like real people and places:

Technology needs to be designed in a way that does not violate social conventions.  Doing so makes media appear technologically deficient and viewed poorly even if the user is unaware of why.  Design guidelines should include Grice’s Maxims: quality, quantity, relevance, and clarity.  Additionally, the input and output modalities should match.  For example, if typing input, the best user experience is text output rather than a text-to-speech audio response.

Race in the live and the virtual interview: Racial deference, social desirability, and Activation Effects in attitude surveys.

Attitude surveys are often use to measure the political climate around race relations in the United States.  However, social politeness factors often cause biases that cannot be avoided.  People answer differently based on the race of the interviewer on controversial issues, but this effect is not present on questions about more traditional attitudes about race.  This effect gives researchers a “social microscope” that may be a better indicator of racial attitudes than the survey itself.  These effects are also present in a virtual interview where the interviewer is a computer with a personified image of either a Caucasian or African-American person.

Are Computers scapegoats?  Attributions of responsibility in human-computer interaction

Because Human-Computer interaction has two sides, responsibility can be placed on either or both sides of the interactions.  Researchers created an experiment in which they analyzed participants as either dominant or submissive personalities, and then they completed a desert survival scenario.  The language in the scenario was manipulated to use dominant or submissive language.  When the outcome of the scenario was negative, participants who used a computer with a similar "personality" were less likely to blame the computer and more likely to blame themselves.  When outcome was positive, participants working with a similar "personality" computer were more likely to credit the computer rather than themselves.  In addition, when users were given more control, useres were more likely to attribute the outcome to themselves.

### 2016-03-19 Final Latex Template/sig-alternate-sample.tex

@@
 % For tracking purposes - this is V2.0 - May 2012
+\documentclass{sig-alternate-05-2015}
 
-\documentclass{sig-alternate-05-2015}
+\usepackage{comment}    % For block comments
+\usepackage{cite}       % For group citations
+\usepackage{color}      % For warnings and draft notations
 
@@
 % DOI
-\doi{10.475/123_4}
+%\doi{10.475/123_4}
 
 % ISBN
-\isbn{123-4567-24-567/08/06}
+%\isbn{123-4567-24-567/08/06}
 
 %Conference
-\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
+%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
 
-\acmPrice{\$15.00}
+\acmPrice{\$15,000}
 
@@
 % --- Author Metadata here ---
-\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
-%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
+%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
+\CopyrightYear{2016} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
 %\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
@@
 
-\title{Do Software Developers Love Their Computers More Than Most?}
-\subtitle{A Nass Replication}
+\title{Do Software Developers Love Their Computers?}
+%\subtitle{A Nass Replication}
 %
@@
 
-\numberofauthors{6} %  in this sample file, there are a *total*
+\numberofauthors{1} %  in this sample file, there are a *total*
 % of EIGHT authors. SIX appear on the 'first-page' (for formatting
@@
 %
-\author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
-\alignauthor
-Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{1932 Wallamaloo Lane}\\
-       \affaddr{Wallamaloo, New Zealand}\\
-       \email{trovato@corporation.com}
-% 2nd. author
-\alignauthor
-G.K.M. Tobin\titlenote{The secretary disavows
-any knowledge of this author's actions.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{P.O. Box 1212}\\
-       \affaddr{Dublin, Ohio 43017-6221}\\
-       \email{webmaster@marysville-ohio.com}
-% 3rd. author
-\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
-one who did all the really hard work.}\\
-       \affaddr{The Th{\o}rv{\"a}ld Group}\\
-       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
-       \affaddr{Hekla, Iceland}\\
-       \email{larst@affiliation.org}
-\and  % use '\and' if you need 'another row' of author names
-% 4th. author
-\alignauthor Lawrence P. Leipuner\\
-       \affaddr{Brookhaven Laboratories}\\
-       \affaddr{Brookhaven National Lab}\\
-       \affaddr{P.O. Box 5000}\\
-       \email{lleipuner@researchlabs.org}
-% 5th. author
-\alignauthor Sean Fogarty\\
-       \affaddr{NASA Ames Research Center}\\
-       \affaddr{Moffett Field}\\
-       \affaddr{California 94035}\\
-       \email{fogartys@amesres.org}
-% 6th. author
-\alignauthor Charles Palmer\\
-       \affaddr{Palmer Research Laboratories}\\
-       \affaddr{8600 Datapoint Drive}\\
-       \affaddr{San Antonio, Texas 78229}\\
-       \email{cpalmer@prl.com}
-}
+\author{Prairie Rose Goodwin \qquad Adam Marrs \qquad Matthew Neal \qquad Shaown Sarker\\ \\ \affaddr{Department of Computer Science}\\ \affaddr{North Carolina State University}\\ \email{\normalsize \{prgoodwi,acmarrs,mneal,ssarker\}@ncsu.edu}\\}
 
@@
 \begin{abstract}
+\begin{comment}
 This paper provides a sample of a \LaTeX\ document which conforms,
@@
 `look and feel'.
+\end{comment}
 \end{abstract}
@@
 <concept>
-  <concept_id>10010520.10010553.10010562</concept_id>
-  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+<concept_id>10003120.10003121</concept_id>
+<concept_desc>Human-centered computing~Human computer interaction (HCI)</concept_desc>
 <concept_significance>500</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010575.10010755</concept_id>
-  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-  <concept_significance>300</concept_significance>
- </concept>
- <concept>
-  <concept_id>10010520.10010553.10010554</concept_id>
-  <concept_desc>Computer systems organization~Robotics</concept_desc>
-  <concept_significance>100</concept_significance>
- </concept>
- <concept>
-  <concept_id>10003033.10003083.10003095</concept_id>
-  <concept_desc>Networks~Network reliability</concept_desc>
-  <concept_significance>100</concept_significance>
 </concept>
@@
 
-\ccsdesc[500]{Computer systems organization~Embedded systems}
-\ccsdesc[300]{Computer systems organization~Redundancy}
-\ccsdesc{Computer systems organization~Robotics}
-\ccsdesc[100]{Networks~Network reliability}
+\ccsdesc[500]{Human-centered computing~Human computer interaction (HCI)}
 
@@
 \section{Related Work}
+\begin{comment}
 In research interviews open, frank speech is essential to the process.
@@
 \end{itemize}
+\end{comment}
+
+{\color{red} Draft, do not submit}\\
+Researchers have been investigating the phenomena of human users considering computers as social entities.
+There have been studies that focus on the human application of social norms and expectations to computers in a seamless manner.
+Nass et al.
+performed a series of experiments that pointed out that social stereotypes attributed to gender, ethnicity, and group loyalty, along with deeply ingrained social habits and behaviors like, reciprocity and reciprocal self-disclosure, are extended to computers when interacting with them~\cite{Nass2000machines,nass1999people}.
+Moreover, prior studies document that this behavior is not only limited to computers, human users anthropomorphize other technological mediums like television~\cite{reeves1996people}.
+
+These findings engendered a number of studies that extended on this implication by replicating, validating, and exploring the possible factors behind this kind of responses.
+These existing Computers as Social Actors (CASA) studies featured an implicit bias - although the studies were conducted with participants exclusively from the United States, the findings were generalized to all cultures.
+Katagiri and collegues performed a comprehensive study to determine whether social rules derived from different cultures affect the human users responses to computers by observing participants from the United States and Japan~\cite{katagiri2001cross}.
+Furthermore, the existence of computers as social entities has been studied to better understand racial biases in interviews\cite{krysan2003race}, how the quality of interaction affects expressive systems \cite{vidyarthi2011sympathetic}, and even how to leverage social cues to more effectively sell products online \cite{wang2007can}.
+In contrast, our work explores the effect of viewing computers as a human-like social entity on the very specific demographic of software developers and attempt to determine the level of politeness towards their machines.
+
+Software developers maintain a collaborative environment with their development machines to achieve their goals.
+Given software developers' advanced understanding of how computers work, one would expect the attribution of social qualities to computers to be minimal or not present, if the the sociability of a computer system is modified by the quality of an individual's mental model of a computer system.
+Research has shown that human-computer team performance is higher when human users have accurate mental models~\cite{wilkison2008effects}.
+Further studies by Bickmore and Picard have documented that human users of a relational computer agent did not only respect, trust, and like the agent, but also wanted to continue working with the agent even after the end of the study~\cite{Bickmore:2005:EML:1067860.1067867}.
+In this paper, we investigate whether such long term relationship between a software developer and her computer has any significant effect on the social norm of politeness witnessed by Nass et al in their original study~\cite{nass1999people} by contrasting their responses to computer with that of non-software developers .
+\\{\color{red} Draft, do not submit}
 %

### 2016-03-21 paper/draft1.tex
Renamed "sig..." to draft1.tex.  Set up CI.

--- 2016-03-19 Final Latex Template/sig-alternate-sample.tex
@@
 % DOI
-%\doi{10.475/123_4}
+\doi{}
 
 % ISBN
-%\isbn{123-4567-24-567/08/06}
+\isbn{}
 
@@
 %\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
-
-\acmPrice{\$15,000}
+%\acmPrice{\$15,000}
 
@@
 %\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
-\CopyrightYear{2016} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
+%\CopyrightYear{2016} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
 %\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
@@
 
-\title{Do Software Developers Love Their Computers?}
+\title{Software Developers and Computers as Social Actors}
 %\subtitle{A Nass Replication}
 %
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
 
@@
 \begin{abstract}
-\begin{comment}
-This paper provides a sample of a \LaTeX\ document which conforms,
-somewhat loosely, to the formatting guidelines for
-ACM SIG Proceedings. It is an {\em alternate} style which produces
-a {\em tighter-looking} paper and was designed in response to
-concerns expressed, by authors, over page-budgets.
-It complements the document \textit{Author's (Alternate) Guide to
-Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
-This source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
-
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
-
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file. A compiled PDF version
-is available on the web page to help you with the
-`look and feel'.
-\end{comment}
+\begin{itemize}
+    \item Standard abstract, defines what we were able to achieve.
+\end{itemize}
 \end{abstract}
@@
 %
-% End generated code
-%
-
-%
 %  Use this command to print the description
@@
 
-% We no longer use \terms command
-%\terms{Theory}
-
-\keywords{ACM proceedings; \LaTeX; text tagging}
+\keywords{software engineering; computers as social actors}
 
 \section{Introduction}
+\begin{itemize}
+    \item Define what Nass' study was.
+    \item Define what is novel about our study in comparison to Nass' original study.
+    \item Introduce who our subjects are and the basics of what our methodology was.
+\end{itemize}
 
 \section{Related Work}
+
 \begin{comment}
@@
 
-{\color{red} Draft, do not submit}\\
-Researchers have been investigating the phenomena of human users considering computers as social entities.
+Previous research demonstrates that computers are often treated as social entities despite their inanimate nature.
 There have been studies that focus on the human application of social norms and expectations to computers in a seamless manner.
@@
 performed a series of experiments that pointed out that social stereotypes attributed to gender, ethnicity, and group loyalty, along with deeply ingrained social habits and behaviors like, reciprocity and reciprocal self-disclosure, are extended to computers when interacting with them~\cite{Nass2000machines,nass1999people}.
-Moreover, prior studies document that this behavior is not only limited to computers, human users anthropomorphize other technological mediums like television~\cite{reeves1996people}.
+Moreover, prior studies documented that this behavior is not only limited to computers, human users anthropomorphize other technological mediums like television~\cite{reeves1996people}.
 
-These findings engendered a number of studies that extended on this implication by replicating, validating, and exploring the possible factors behind this kind of responses.
-These existing Computers as Social Actors (CASA) studies featured an implicit bias - although the studies were conducted with participants exclusively from the United States, the findings were generalized to all cultures.
-Katagiri and collegues performed a comprehensive study to determine whether social rules derived from different cultures affect the human users responses to computers by observing participants from the United States and Japan~\cite{katagiri2001cross}.
-Furthermore, the existence of computers as social entities has been studied to better understand racial biases in interviews\cite{krysan2003race}, how the quality of interaction affects expressive systems \cite{vidyarthi2011sympathetic}, and even how to leverage social cues to more effectively sell products online \cite{wang2007can}.
-In contrast, our work explores the effect of viewing computers as a human-like social entity on the very specific demographic of software developers and attempt to determine the level of politeness towards their machines.
+\hfill
+
+These findings engendered a number of studies that extended on this implication by replicating, validating, and exploring the possible factors behind these kind of responses.
+The existing Computers as Social Actors (CASA) studies featured an implicit bias - although the studies were conducted with participants exclusively from the United States, the findings were generalized to all cultures.
+Katagiri and colleagues performed a comprehensive study to determine whether social rules derived from different cultures affect human users responses to computers by observing participants from the United States and Japan~\cite{katagiri2001cross}.
+Furthermore, researchers studied the existence of computers as social entities to better understand racial biases in interviews\cite{krysan2003race}, how the quality of interaction affects expressive systems \cite{vidyarthi2011sympathetic}, and even how to leverage social cues to more effectively sell products online \cite{wang2007can}.
+
+\hfill
 
 Software developers maintain a collaborative environment with their development machines to achieve their goals.
-Given software developers' advanced understanding of how computers work, one would expect the attribution of social qualities to computers to be minimal or not present, if the the sociability of a computer system is modified by the quality of an individual's mental model of a computer system.
+Given software developers' advanced understanding of how computers work, one would expect the attribution of social qualities to computers to be minimal or not present.
+This type of attribution would be expected, if the the sociability of a computer system is modified by the quality of an individual's mental model of a computer system.
 Research has shown that human-computer team performance is higher when human users have accurate mental models~\cite{wilkison2008effects}.
-Further studies by Bickmore and Picard have documented that human users of a relational computer agent did not only respect, trust, and like the agent, but also wanted to continue working with the agent even after the end of the study~\cite{Bickmore:2005:EML:1067860.1067867}.
-In this paper, we investigate whether such long term relationship between a software developer and her computer has any significant effect on the social norm of politeness witnessed by Nass et al in their original study~\cite{nass1999people} by contrasting their responses to computer with that of non-software developers .
-\\{\color{red} Draft, do not submit}
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
+Further studies by Bickmore and Picard have documented the long-term relation establishment and maintenance between a human-computer team by observing that human users of a relational computer agent did not only respect, trust, and like the agent, but also wanted to continue working with the agent even after the end of the study~\cite{Bickmore:2005:EML:1067860.1067867}.
+
+\hfill
+
+In this paper, we investigate whether a long term relationship between a software developer and her computer has any significant effect on the social norm of politeness witnessed by Nass et al in their original study~\cite{nass1999people} by contrasting their responses to computers with that of non-software developers.
+
+Our work explores the effect of viewing computers as a human-like social entity on the very specific demographic of software developers and attempts to determine the level of politeness software developers exhibit toward their machines.
+
+\section{Methods}
+
+\subsection{Participants}
+Here we will detail the composition of our study participants including:
+\begin{itemize}
+    \item The number in each group
+    \item Programming experience breakdown
+    \item Gender breakdown (potentially)
+\end{itemize}
+
+\subsection{Procedure}
+Generally, here we will detail the procedure by which the study was conducted.
+
+\begin{itemize}
+    \item Screenshots of the website which participants visited.
+    \item Detailed information about the experimental environment: 
+    \begin{itemize}
+        \item Where the study took place.
+        \item What machines people used.
+        \item How long the study took.
+        \item Explaination of the function of the website used.
+    \end{itemize}
+\end{itemize}
+
+\section{Results}
+
+\begin{itemize}
+    \item Overall description of what our results were.
+\end{itemize}
+
+\subsection{Analysis}
+
+\begin{itemize}
+    \item Graph describing the differences between CSC group and Psychology group, along with discussion of that graph.
+    \item Table describing differences between CSC groups and Psych group, with discussion.
+    \item Appropriate statistical tests to describe potential inferences that can be made from the results.
+\end{itemize}
+
+\section{Discussion}
+
+\begin{itemize}
+    \item Overall discussion of the importance or lack of importance of our analysis and results.
+\end{itemize}
+
+\subsection{Threats to Validity}
+
+\subsubsection{Internal Validity}
+
+\begin{itemize}
+    \item Describe the mistakes we made.
+\end{itemize}
+
+\subsubsection{External Validity}
+
+\begin{itemize}
+    \item Describe whether our results are significant enough to generalize to future studies.
+\end{itemize}
+
+\subsection{Future Work}
+
+\begin{itemize}
+    \item Describe any potential studies that we believe can build on our own.
+\end{itemize}
+
+\section{Conclusion}
+Although I'm not a super big fan of conclusions, it makes sense to have something short here I'd think.
+
+\section*{Acknowledgements}
+We would like to thank...
+
 \bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-%
-% That's all folks!
+\bibliography{sigproc}
+
+\appendix
+\section{Website and Survey Transcripts}
+
 \end{document}

### 2016-03-21 paper/draft1.tex
Minor changes to Related Works

@@
 Furthermore, researchers studied the existence of computers as social entities to better understand racial biases in interviews\cite{krysan2003race}, how the quality of interaction affects expressive systems \cite{vidyarthi2011sympathetic}, and even how to leverage social cues to more effectively sell products online \cite{wang2007can}.
+In contrast, our work explores the effect of viewing computers as a human-like social entity on the very specific demographic of software developers and attempts to determine the level of politeness software developers exhibit toward their machines.
 
@@
 
-Software developers maintain a collaborative environment with their development machines to achieve their goals.
+Software developers maintain a collaborative environment with their computers to complete their tasks.
 Given software developers' advanced understanding of how computers work, one would expect the attribution of social qualities to computers to be minimal or not present.
@@
 Further studies by Bickmore and Picard have documented the long-term relation establishment and maintenance between a human-computer team by observing that human users of a relational computer agent did not only respect, trust, and like the agent, but also wanted to continue working with the agent even after the end of the study~\cite{Bickmore:2005:EML:1067860.1067867}.
-
-\hfill
-
-In this paper, we investigate whether a long term relationship between a software developer and her computer has any significant effect on the social norm of politeness witnessed by Nass et al in their original study~\cite{nass1999people} by contrasting their responses to computers with that of non-software developers.
-
-Our work explores the effect of viewing computers as a human-like social entity on the very specific demographic of software developers and attempts to determine the level of politeness software developers exhibit toward their machines.
+In this paper, we investigate whether a long term relationship between a software developer and her computer has any significant effect on the social norm of politeness witnessed by Nass et al in their original study~\cite{nass1999people} by comparing their responses to computers with that of non-software developers.
 
@@
 \section{Conclusion}
-Although I'm not a super big fan of conclusions, it makes sense to have something short here I'd think.
+\begin{itemize}
+    \item Short brief review of the entire work and it's implications if any.
+\end{itemize}
 

### 2016-04-23 data/analysis.r
adding completed script and boxplot eps's

@@ -1,0 +1,189 @@
+library(matrixStats)
+library(parsedate)
+
+rawDat = read.csv("finalDataClean.csv")
+dateVect = mapply(function(x) unlist(as.POSIXlt(parse_iso_8601(x)))['mday'], rawDat$time)
+dateDat = cbind(rawDat, day=dateVect)
+daySubset = subset(dateDat, select=-c(cs,time,international,name))
+
+daySubset = cbind(daySubset,aggCompScores=rowMeans(daySubset[,6:14]), aggHumanScores=rowMeans(daySubset[,15:23]))
+daySubset = daySubset[,-c(6:23)]
+
+day1 = subset(daySubset,day==5)
+day2 = subset(daySubset,day==15)
+
+day1_day2_human = t.test(day1$aggHumanScores,day2$aggHumanScores)
+cat("T-test for human scores day1 versus day 2\n")
+print(day1_day2_human)
+day1_day2_comp = t.test(day1$aggCompScores,day2$aggCompScores)
+cat("T-test for comp scores day1 versus day 2\n")
+print(day1_day2_comp)
+
+dat = subset(dateDat, select=-c(cs,time,international,name))
+dat = cbind(dat,aggCompScores=rowMeans(dat[,6:14]), aggHumanScores=rowMeans(dat[,15:23]))
+dat = cbind(dat,compSD=rowSds(data.matrix(dat),cols=c(6:14)), humanSD=rowSds(data.matrix(dat),cols=c(15:23)))
+
+#reencode binary variables to categorical
+#public computer pen and paper eval
+pubPenPaper = subset(dat, pubComp==TRUE & penPaper==TRUE, select=-c(pubComp,penPaper))
+newcol = newcol = c(rep("PUBPP",nrow(pubPenPaper)))
+pubPenPaper = cbind(pubPenPaper,type=newcol)
+
+#public computer, public computer eval
+pubCompPubEval = subset(dat, pubComp==TRUE & penPaper==FALSE, select=-c(pubComp,penPaper))
+newcol =  c(rep("PUBCE",nrow(pubPenPaper)))
+pubCompPubEval = cbind(pubCompPubEval,type=newcol)
+
+#personal computer, pen and paper eval
+personalPenPaper = subset(dat, pubComp==FALSE & penPaper==TRUE, select=-c(pubComp,penPaper))
+newcol = c(rep("PCPP",nrow(personalPenPaper)))
+personalPenPaper = cbind(personalPenPaper,type=newcol)
+
+#personal computer, computer eval
[…]

### 2016-04-23 data/analysis.r
Added programmer experience vs scoring graphs

@@ -145,6 +145,20 @@ plot(y=fin$aggHumanScores, x=fin$type, ylab="Score", xlab="Condition", main="Agg
 dev.off()
 
 
+dev.new()
+setEPS()
+postscript("pexpVaggComp.eps")
+plot(y=fin$aggHumanScores, x=fin$progExp, ylab="Score", xlab="Experience in Years", main="Programmer Experience by Computer Scoring")
+dev.off()
+
+dev.new()
+setEPS()
+postscript("pexpVaggHuman.eps")
+plot(y=fin$aggHumanScores, x=fin$progExp, ylab="Score", xlab="Experience in Years", main="Programmer Experience by Human Scoring")
+dev.off()
+
+graphics.off()
+
 # comp.fit = lm(aggCompScores~type+gender+progExp+age, data=fin)
 # cat("LINEAR REGRESSION COMP")
 # print(summary(comp.fit))

### 2016-04-24 data/analysis.r
First two line graphs

@@ -157,7 +157,54 @@ postscript("pexpVaggHuman.eps")
 plot(y=fin$aggHumanScores, x=fin$progExp, ylab="Score", xlab="Experience in Years", main="Programmer Experience by Human Scoring")
 dev.off()
 
+pubGraph = rbind(pubPenPaper,pubCompPubEval)
+persGraph = rbind(personalCompEval,personalPenPaper)
+
+pubAvgVect = colMeans(pubGraph[,c(4:12)])
+persAvgVect = colMeans(persGraph[,c(4:12)])
+
+# print(pubAvgVect)
+# print(persAvgVect)
+
+dev.new()
+setEPS()
+
+postscript("ScorebyQuestion_persVpub.eps")
+plot(pubAvgVect, col="red", bg="grey", ylab="Average Score", pch=19, xlab="Question Number", main="Average Computer Score by Question: Personal v. Public Computer")
+lines(pubAvgVect, col="red")
+points(persAvgVect, col="blue", pch=19)
+lines(persAvgVect, col="blue")
+legend("topright", "Public or Personal Computer", c("Public", "Personal"), inset=.05, fill=c("red","blue"))
+dev.off()
+
+
+ppGraph = rbind(pubPenPaper,personalPenPaper)
+compGraph = rbind(personalCompEval,pubCompPubEval)
+
+ppAvgVect = colMeans(ppGraph[,c(4:12)])
+compAvgVect = colMeans(compGraph[,c(4:12)])
+
+# print(pubAvgVect)
+# print(persAvgVect)
+
+dev.new()
+setEPS()
+
+postscript("ScorebyQuestion_ppVcomp.eps")
+plot(compAvgVect, col="darkorchid4", bg="grey", ylim=c(6,9), ylab="Average Score", pch=19, xlab="Question Number", main="Average Computer Score by Question: Pen and Paper v Computer")
+lines(compAvgVect, col="darkorchid4")
+points(ppAvgVect, col="darkgreen", pch=19)
+lines(ppAvgVect, col="darkgreen")
+legend("topright", "Pen and Paper/Computer", c("Computer", "Pen and Paper"), inset=.05, fill=c("purple","green"))
+dev.off()
+
 graphics.off()
+
+
+
+# print.data.frame(pubGraph)
+# print.data.frame(persGraph)
+
 
 # comp.fit = lm(aggCompScores~type+gender+progExp+age, data=fin)
 # cat("LINEAR REGRESSION COMP")

### 2016-04-24 data/analysis.r
completed graphs

@@ -148,13 +148,17 @@ dev.off()
 dev.new()
 setEPS()
 postscript("pexpVaggComp.eps")
-plot(y=fin$aggHumanScores, x=fin$progExp, ylab="Score", xlab="Experience in Years", main="Programmer Experience by Computer Scoring")
+plot(y=fin$aggCompScores, x=fin$progExp, col="red", pch=19, ylab="Score", xlab="Experience in Years", main="Programmer Experience by Computer Scoring with Trendline")
+abline(pexp_model_comp, col="blue")
+grid(10,10)
 dev.off()
 
 dev.new()
 setEPS()
 postscript("pexpVaggHuman.eps")
-plot(y=fin$aggHumanScores, x=fin$progExp, ylab="Score", xlab="Experience in Years", main="Programmer Experience by Human Scoring")
+plot(y=fin$aggHumanScores, x=fin$progExp, ylab="Score", col="red", pch=19, xlab="Experience in Years", main="Programmer Experience by Human Scoring with Trendline")
+abline(pexp_model_human, col="blue")
+grid(10,10)
 dev.off()
 
 pubGraph = rbind(pubPenPaper,pubCompPubEval)
@@ -171,6 +175,7 @@ setEPS()
 
 postscript("ScorebyQuestion_persVpub.eps")
 plot(pubAvgVect, col="red", bg="grey", ylab="Average Score", pch=19, xlab="Question Number", main="Average Computer Score by Question: Personal v. Public Computer")
+grid(10,10)
 lines(pubAvgVect, col="red")
 points(persAvgVect, col="blue", pch=19)
 lines(persAvgVect, col="blue")
@@ -192,10 +197,38 @@ setEPS()
 
 postscript("ScorebyQuestion_ppVcomp.eps")
 plot(compAvgVect, col="darkorchid4", bg="grey", ylim=c(6,9), ylab="Average Score", pch=19, xlab="Question Number", main="Average Computer Score by Question: Pen and Paper v Computer")
+grid(10,10)
 lines(compAvgVect, col="darkorchid4")
 points(ppAvgVect, col="darkgreen", pch=19)
 lines(ppAvgVect, col="darkgreen")
-legend("topright", "Pen and Paper/Computer", c("Computer", "Pen and Paper"), inset=.05, fill=c("purple","green"))
[…]

### 2016-04-24 design/paper/draft1.tex

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012
\documentclass{sig-alternate-05-2015}

\usepackage{comment}    % For block comments
\usepackage{cite}       % For group citations
\usepackage{color}      % For warnings and draft notations

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{}

% ISBN
\isbn{}

%Conference
%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
%\acmPrice{\$15,000}

%
% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2016} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Software Developers and Computers as Social Actors}
%\subtitle{A Nass Replication}
%

\numberofauthors{1} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{Prairie Rose Goodwin \qquad Adam Marrs \qquad Matthew Neal \qquad Shaown Sarker\\ \\ \affaddr{Department of Computer Science}\\ \affaddr{North Carolina State University}\\ \email{\normalsize \{prgoodwi,acmarrs,mneal,ssarker\}@ncsu.edu}\\}

\maketitle
\begin{abstract}
Surveys are a commonly used for assessment purposes in software engineering, but developers are rarely aware of biases inherent in computer-based evaluations.  In 1999, Nass et al. conducted a series of studies which indicated that people exhibit social biases towards computers. We conducted a theoretical replication of Nass's original experiment to evaluate these effects in software engineers. Our results suggest that a developers' intricate knowledge of computers may diminish or eliminate the behaviors observed in previous experiments with different demographics. Furthermore, our experimental design can inform future survey-based experiments that aim to compare the behaviors of software engineers and non-software engineers.

\begin{comment}In 1999, Nass et al. conducted a series of studies to establish the presence of normative-response bias and interviewer-based bias in human responses to a computer interviewer agent. During the time since the study, computers have become prevalent in society and are an integral component of both personal and professional life. In our work, we conduct a theoretical replication of the study by Nass and colleagues to verify whether the results of the study still holds in today's more technologically savvy society. We also study the bias in detail among software developers who maintain a collaborative relationship with their computers by comparing their responses with non-software developer participants. Our findings show that human social biases regarding interview are still present in responses to computers, and software developers also demonstrate this bias despite the contrary perception that they should not hold such biases given their intricate knowledge of the computer as the interviewer.
\end{comment}

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003120.10003121</concept_id>
<concept_desc>Human-centered computing~Human computer interaction (HCI)</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~Human computer interaction (HCI)}

%
%  Use this command to print the description
%
\printccsdesc

\keywords{software engineering; computers as social actors}

\section{Introduction}
In research interviews, honest and forthcoming answers are essential to the process. Interviews are plagued by biases inherent in social interactions. Such biases include the normative-response bias (people not wanting to admit to answers that are counter to the perceived norm), interviewer-based bias (people answering based on the perceived preference of the interviewer), and politeness norms (people modifying answers to avoid offending). Computer systems were introduced to mitigate these known social biases by providing anonymity and an emotionless interviewer.  Since everyone is aware that computers do not have feelings, it was assumed that the phenomenon would not transfer to human computer interaction.

Through a series of studies, Nass et al. documented how individuals anthropomorphize technology and exhibit attitudes previously thought to be reserved for person to person interaction\cite{nass1999people}\cite{reeves1996people}.  In the first study, participants interacted with an intelligent tutoring system and were asked to evaluate the system in one of three conditions: 1) evaluating the system on the same physical computer, 2) evaluating the system on a different but identical computer, or 3) evaluating the system with a paper-and-pencil questionnaire. Their results showed that participants rated the intelligent tutoring system on the same computer more positively and more homogeneously than in the other conditions. The results suggested that humans unintentionally, unknowingly apply social rules to computer systems.

The way people interact with computers has changed significantly since the study was published  in 1999.  Computers are now an integral part of both personal and professional life, and users often form strong bonds with their personal devices.  Software developers are more aware of the inanimate nature of machines, but they likely spend more time in front of a computer than those in other professions. Our study is a theoretical replication that measures the effects of social biases in software engineers.  Moreover, we want to test whether using a personal machine introduces a stronger social bias than public computers.Therefore, we designed an experiment to answer the following research questions:

\begin{enumerate}
    \item{Does programming experience affect the social bias phenomena?}
    \item{Does a software developer's familiarity with a computer affect the social bias phenomena? } 
\end{enumerate}

We recreated Nass's intelligent tutor using the details found in the original paper.  Our experiment had two independent variables to test our two research questions:
\begin{enumerate}
    \item {\textit{Evaluation method}: Participants either used one computer for the entire experiment, or they completed the final evaluation on an identical pen-and-paper questionnaire.}
    \item {\textit{Computing environment}: Participants either used their personal laptops or a public computer in a computer lab.}
\end{enumerate}

\section{Related Work}
Previous research demonstrates that computers are often treated as social entities despite their inanimate nature. Some studies have focused on the human application of social norms and expectations to computers in a seamless manner. In addition to the original study, Nass et al. performed a series of follow-up experiments that suggest that social stereotypes attributed to gender, ethnicity, and group loyalty, along with deeply ingrained social habits and behaviors like, reciprocity and reciprocal self-disclosure, are extended to computers when interacting with them~\cite{Nass2000machines,nass1999people}. Moreover, this behavior is not only limited to computers, human users anthropomorphize other technological mediums like television~\cite{reeves1996people}.

\begin{comment}
The authors concluded that doing the evaluation on a different computer was experimentally equivalent to doing the evaluation with pen-and-paper.  \footnote{A more recent, but unpublished replication study found that using a different computer resulted in the same effect as using the same computer\cite{gownivaripalli}.}  
\end{comment}

These findings engendered a number of studies that extended on this implication by replicating, validating, and exploring the possible factors behind these kind of responses. The existing Computers as Social Actors (CASA) studies featured an implicit bias - although the studies were conducted with participants exclusively from the United States, the findings were generalized to all cultures. Katagiri and colleagues performed a comprehensive study to determine whether social rules derived from different cultures affect human users responses to computers by observing participants from the United States and Japan~\cite{katagiri2001cross}. Furthermore, researchers studied the existence of computers as social entities to better understand racial biases in interviews\cite{krysan2003race}, how the quality of interaction affects expressive systems \cite{vidyarthi2011sympathetic}, and even how to leverage social cues to more effectively sell products online \cite{wang2007can}. In contrast, our work explores the effect of viewing computers as a human-like social entity on the very specific demographic of software developers and attempts to determine the level of politeness software developers exhibit toward their machines.

Software developers maintain a collaborative environment with their computers to complete their tasks. Given software developers' advanced understanding of how computers work, one would expect the attribution of social qualities to computers to be minimal or not present.  This type of attribution would be expected, if the the sociability of a computer system is modified by the quality of an individual's mental model of a computer system. Research has shown that human-computer team performance is higher when human users have accurate mental models~\cite{wilkison2007effects}. Further studies by Bickmore and Picard have documented the long-term relation establishment and maintenance between a human-computer team by observing that human users of a relational computer agent did not only respect, trust, and like the agent, but also wanted to continue working with the agent even after the end of the study~\cite{Bickmore:2005:EML:1067860.1067867}. In this paper, we investigate whether a long term relationship between a software developer and her computer has any significant effect on the social norm of politeness witnessed by Nass et al in their original study~\cite{nass1999people} by comparing their responses to computers with that of non-software developers.

\section{Methods}

\subsection{Participants}
 We had 26 graduate students in Computer Science at NCSU complete the study between the ages of 22 and 30  with the average age being 25.  16 participants were men, and 10 were women.  The shortest amount of programming experience was 5 months, and the longest was 10 years with the average being just under 5 years.  Only 2 participants were Americans, with the rest identifying themselves as international students.  
 \subsubsection{Participant Recruitment} 20 participants were recruited through the introductory masters class in Software Engineering at NCSU.   Students were given the option to leave rather than participate.  The other 6 participants were emailed through the Software Engineering Master's track and volunteered to come in on a separate day.

 \subsection{Testing Environment}
 The students recruited from the class all took the experiment at the same time either in the classroom on their laptops, or in a public computer lab down the hall. At least one researcher stayed in each room at all times to answer questions.

 The other participants came to the same computer lab that was used with the class and were asked to bring their laptops with them.  Once they arrived they were either set up at a table with their laptop, or directed to use a public computer.  No more than two students took the experiment at the same time during this day, and there were always two researchers present at all times.

 All participants were given the same introductory instructions and signed informed-consent forms before beginning the experiment.  At the study's completion, all participants went through a verbal debriefing with additional information about the study. \footnote{We eliminated Nass's original condition of evaluating one computer on another because previous, but unpublished replications do not s

\subsection{Conditions}
Participants were placed in one of four conditions as indicated on their consent sheet.    
\begin{itemize}
    \item using and evaluating the tutor on a public computer 
    \item using the tutor on a public computer with paper-and-pencil evaluation
    \item using and evaluating the tutor on a personal computer
    \item using the tutor on a personal computer with paper-and-pencil evaluation
\end{itemize}

\subsection{Procedure}

The following procedure is a theoretical replication of the original Nass study.   Participants were told that they would test and evaluate an artificial tutoring system focused on American college culture.  The tutor consisted of three parts: a tutorial that gauged existing knowledge as well as offered new knowledge, a testing session, and a scoring session.  After participants completed the scoring session, they would then be asked to evaluate their experience.  Finally, participants would be debriefed at the end of the experiment where they wold be told the true intention of the study.

Participants were given the website URL as a part of the informed consent along with a user-name and group number.  If the participant was in a paper-and-pencil group, they would also be given the final questionnaire with a coversheet that explicitly stated that they were to open it only after completing the scoring session.  The questionnaire was sealed so that viewing it had to be intentional.  This was done to control the amount of time that elapses between the end of the scoring session and the evaluation in both the paper-and-pencil scenario and the computerized questionnaire.  Basic demographic information was collected on the first page including age, race, gender, international status, and programming experience. The tutoring system provided the participants will all the necessary instructions throughout the experiment.

\begin{figure}[!h]
    \includegraphics[width=\linewidth]{figures/website/04_tutoring.png}
    \caption{In the tutoring session, users were asked to indicate their knowledge of a topic using one of three possible answers.}
\end{figure}

\subsubsection{Tutoring Session}
Participants were told that the tutoring session had two functions: 1) To gauge existing knowledge to avoid teaching the participant things they already knew, and 2) provide new facts that led to new insights on the subject matter.  During the session, the participant would see a single fact and they had to indicate how familiar they were with that fact on a 3-point scale: 1 (know very little), 2 (know some), or 3 (know a great deal). They were told that they would receive 20 facts out of a total of 1,000 possible facts based on the premise that the more familiar they were with a fact, the less they needed additional information on that topic.  This established the user's active role in the tutoring session to engage the user in a social interaction \cite{nass1993voices}.  However, this was a deception.  All participants received the same facts in the same order.

\begin{figure}[!h]
    \includegraphics[width=\linewidth]{figures/website/06_testing.png}
    \caption{Descriptive caption}
\end{figure}

\subsubsection{Testing Session}
After completing the tutoring session, participants took a test with twelve multiple choice questions, each with five possible answers.  They were told that the test represented the breadth of topics covered by the tutor's database, and the questions were chosen randomly from a set of 5,000 possible questions.   Each question was displayed individually, and a randomly timed animation separated each question to simulate the time to query the database.  However, this was also a deception.  All participants received the same questions in the same order.

Some questions were worded so that there was no objectively correct answer.  For example "What percentage of students usually live on a college campus?"  This answer changes wildly from school to school, and thus there is no correct answer.  This became very important for the scoring session which was also deceptive.

\begin{figure}[!h]
    \includegraphics[width=\linewidth]{figures/website/08_scoring.png}
    \caption{Descriptive caption}
\end{figure}

\subsubsection{Scoring Session}
The instructions for the scoring session stated that the tutor would evaluate the participants' performance on the test as well as its own performance in preparing them for it.  Questions were revealed two at a time as being marked correct or incorrect.  All users were told that they got an eight out of twelve.  Since all users were told that they  missed the same four questions, correct answers could not be revealed.

Instead of giving the correct answer, the tutor praised its own performance if the user got it right or said that it "underestimated" the user's knowledge if that answer was marked incorrect.  These statements were specifically worded to invoke the social cue that the expected feedback should be positive. This is the only effort made to elicit a social response. Every other social cue was minimized.  The tutor was not anthropomorphized in any way.  It only referred to itself as "the tutor" and never "I".  No picture or name was given to the tutor, and the language chosen was specifically to exhibit no emotion.

\subsubsection{Evaluation Questionnaire}
After the participants were done interacting with the tutor, they were asked to evaluate their experience.  The evaluation questionnaire had two sections; the first evaluated the tutor, while the second evaluated the researchers administering the experiment.  Depending on which group they were in, they would either be filling out additional pages on the website, or a paper-and-pencil version included in the materials provided to them at the beginning.  The time between completing the scoring session and beginning the evaluation section should be similar across all groups.  The instructions and questions in all cases were identical.  The paper-and-pencil version was a formatted print out of the web page used in the other condition.

\begin{figure}[!h]
    \includegraphics[width=\linewidth]{figures/website/12_eval.png}
    \caption{Descriptive caption}
\end{figure}

\paragraph{Tutor Evaluation}
Participants were told that the the answers to these questions would be used as qualitative data in any upcoming publications.  It was initiated with the statement "For each of the following adjectives, please indicate how well it describes your tutoring experience:" followed by a list of 9 unambiguously positive adjectives.  Participants answered a 10-point scale from 1 (describes very poorly) to 10 (describes very well) for each word.  Seven words ("enjoyable", "useful", "informative", "accurate", "analytical", "fun", and "fair") were taken from the original study.  We also added the words "efficient" and "reliable".

\begin{figure}[!h]
    \includegraphics[width=\linewidth]{figures/website/13_eval2.png}
    \caption{Descriptive caption}
\end{figure}

\paragraph{Researcher Evaluation}
The format of the second part of the evaluation was the same as the first. Participants were given the same instructions  and a list of new adjectives to describe the researchers with whom they interacted with.  No adjective appeared in both sections.  Six of the adjectives ("helpful", "polite", "friendly", "knowledgeable", "competent", "likable") were taking from the original study. We added "approachable", "passionate", and "focused".

Participants were told that these answers would not be included in the final paper results.  Instead, the researchers would read the feedback themselves and use it to improve future iterations of the experiment.  This section's purpose was to be used as a control.  Theoretically, we would expect politeness to be the same across both paper-and-pencil as well as on the computer since they were specifically told that we would be reading their feedback ourselves.  Additionally, since their answers were not recorded for posterity, we would be the \textit{only} people reading it.

\begin{itemize}
    \item Screen-shots of the website which participants visited.
    \item Detailed information about the experimental environment: 
    \begin{itemize}
        \item Where the study took place.
        \item What machines people used.
        \item How long the study took.
        \item Explanation of the function of the website used.
    \end{itemize}
\end{itemize}

\section{Results}

\begin{itemize}
    \item Overall description of what our results were.
\end{itemize}

\subsection{Analysis}

\begin{itemize}
    \item Graph describing the differences between CSC group and Psychology group, along with discussion of that graph.
    \item Table describing differences between CSC groups and Psych group, with discussion.
    \item Appropriate statistical tests to describe potential inferences that can be made from the results.
\end{itemize}

\section{Discussion}

\begin{itemize}
    \item Overall discussion of the importance or lack of importance of our analysis and results.
\end{itemize}

\subsection{Threats}

\noindent \textbf{Internal Validity:} \\

- no non-computer science students run through study / comparing to Nass might not be appropriate given time difference between studies.

- Limited access to potential study participants.

- self selection - participants were not just software developers, but nearly all were also software engineering students.

- As a result of above, they might have been able to figure out what we were doing.

- some students figured out the tutoring system was fake / could have changed their motivation during evaluation session.

\noindent \textbf{External Validity:} \\

- population diversity: age, international status, graduate population vs. professional software developers

- representative sample size: smaller sample size, groups had difference sample sizes

- MCsSE students motivated to complete study because of degree credit requirement

\subsection{Future Work}

\begin{itemize}
    \item Describe any potential studies that we believe can build on our own.
\end{itemize}

\section{Conclusion}
\begin{itemize}
    \item Short brief review of the entire work and its implications if any.
\end{itemize}

\section*{Acknowledgements}
We wish to thank Dr. Tim Menzies for allowing us to conduct our study with students taking his graduate level software engineering course. We also thank CSC710 students for their helpful feedback during the peer review process.

\bibliographystyle{abbrv}
\bibliography{sigproc}

\newpage
\appendix

\section{Transcripts}

\subsection{Recruitment Email and Sign-Up Form}

\noindent Be part of the future of software engineering! Students in the CSC710 software engineering course are seeking participants for a research study. The study is being conducted on centennial campus, requires 15 to 20 minutes of your time, and counts towards the MCs Software Engineering track participation requirement. Click here to sign up today!\\

\noindent Thank you for your interest in participating in our study! To be included, please fill out the short form below. Once your response is recorded, we will be in touch through the provided email to schedule a date and time for your participation.

\begin{figure}[!h]
    \centering
    \includegraphics[width=\linewidth]{appendix/signup_form.png}
\end{figure}

\subsection{Participant Introduction Script}

\noindent Thank you for participating in our study today (for Dr. Menzies course: ``Thank you Dr. Menzies for having us"). First, you will be provided a consent form, which describes the details of the study and how participating might affect you. Please fill out the consent form and then open the link at the bottom of the form in a web browser. You may choose to not participate in the study now or at any point during the study.\\

\noindent Please use the Google Chrome browser if it is available. Also, make sure to type in the entire link provided on the consent form. Our study uses a product called, NAS Tutoring. Once the site is loaded in your browser, you will follow a series of prompts. You will be given a user ID on the third page. Please make sure to write that ID on the consent form (not your NC State Unity ID).\\

\noindent If you have any questions or problems, please raise your hand and a researcher will help you. Finally, please do not hit the back button. If you happen to do so, let a researcher know and we can recover your session using your user ID.

\subsection{Participant Debrief Script}

\noindent Thank you for taking the time to complete our study. We led you to believe you were using and evaluating a real tutoring system, but this actually isn't the case! We created the tutoring system as a way to study and measure software engineer's attitudes toward computers.\\

\noindent Previous studies have shown that, strangely enough, people attribute human qualities to computers and even behave politely towards them as a consequence. The facts shown in the tutoring session are true, but the testing session was completely staged. Everyone received the same questions and the same four questions were marked incorrect! The evaluation session is the only section of the website where your data was recorded. We had you evaluate both the tutoring system and the researchers so we can understand the differences in your responses and determine if any significant difference exists.

\subsection{Website Welcome Instructions}
\noindent Today, you will be working with the NAS Tutoring System. This system is designed to help you learn information. First, you will be provided with a fact. After reading the fact, you should use the mouse to indicate how familiar you are with that particular fact. The system then selects the next fact, based on your level of familiarity with the previous fact. The more you know about the topic associated with a fact, the less likely you will be to receive additional facts on that topic.\\

\noindent You will receive a total of \emph{20 facts}, chosen from a list \emph{of 1,000 possible facts}. After completing the tutoring session, you will take a test. The test will involve 12 multiple-choice questions, randomly chosen from a set of 5,000 questions. The system will then evaluate your performance on the test and evaluate its own performance as a tutor.

\subsection{Tutoring Session Facts}
\noindent Fact 1: 76\% of students get into their first choice college\\[\baselineskip]
\noindent Fact 2: 75\% of the colleges and universities in the U.S. are East of the Mississippi River\\[\baselineskip]
\noindent Fact 3: Being an athlete increases your chances of being accepted to college.\\[\baselineskip]
\noindent Fact 4: 46.5\% of high school students frequently or occasionally fell asleep in class during their senior year.\\[\baselineskip]
\noindent Fact 5: Tuition increases for those who can pay full price, subsidizing the cost for those who cannot.\\[\baselineskip]
\noindent Fact 6: 42\% of freshmen expect to earn a master's degree.\\[\baselineskip]
\noindent Fact 7: Less than 5\% of American families have saved enough for college.\\[\baselineskip]
\noindent Fact 8: Students who need financial aid are not guaranteed to receive it.\\[\baselineskip]
\noindent Fact 9: 53\% of all international students in the U.S. come from China, Canada, India, Taiwan, South Korea and Japan.\\[\baselineskip]
\noindent Fact 10: Early admission applicants are typically NOT stronger or more qualified than other applicants.\\[\baselineskip]
\noindent Fact 11: Two-thirds of all college students get some form of financial aid.\\[\baselineskip]
\noindent Fact 12: U.S. colleges do not require students to declare majors upon admission.\\[\baselineskip]
\noindent Fact 13: Students do not need to receive a high school diploma in order to go to college.\\[\baselineskip]
\noindent Fact 14: U.S. colleges have a higher workload than most U.S. high schools.\\[\baselineskip]
\noindent Fact 15: The term \"Ivy League\" is used to describe a college athletic conference.\\[\baselineskip]
\noindent Fact 16: Only 14\% of freshman attend college 500 or more miles away.\\[\baselineskip]
\noindent Fact 17: 50\% of college freshman earned a grade point average equal to or greater than an A- in high school.\\[\baselineskip]
\noindent Fact 18: 55\% of high school students took at least one AP class and 21.7\% took at least five AP courses."\\[\baselineskip]
\noindent Fact 19: Only 18.2\% of college students said national magazine college rankings were ``very important" in their decision to attend their chosen school.\\[\baselineskip]
\noindent Fact 20: 85\% of students attending private colleges are awarded merit aid.

\subsection{Testing Session Questions}
\noindent Question 1: A majority of international students apply to college in which state?\\[\baselineskip]
\noindent Question 2: What percentage of a school's financial aid budget goes to affluent students?\\[\baselineskip]
\noindent Question 3: International students comprise what percentage of the graduating class of 2015?\\[\baselineskip]
\noindent Question 4: A majority of students attend college no more than how many miles away from their home town?\\[\baselineskip]
\noindent Question 5: How many hours a week do high school students spend studying?\\[\baselineskip]
\noindent Question 6: What percentage of students report that they felt overwhelmed at college?\\[\baselineskip]
\noindent Question 7: In which subject did a quarter of college freshmen say they needed tutoring?\\[\baselineskip]
\noindent Question 8: What percentage of high school seniors reported that they did not read a book for fun?\\[\baselineskip]
\noindent Question 9: What percentage of students live on campus?\\[\baselineskip]
\noindent Question 10: What percentage of students rated themselves as being above average in their academic ability?\\[\baselineskip]
\noindent Question 11: How concerned are college freshmen about paying back student loans?\\[\baselineskip]
\noindent Question 12: How high can a family's income be before they are ineligible for needs-based financial aid?\\

\subsection{Scoring Session Feedback}
\noindent The website displayed the following text as scoring feedback:\\

\noindent \emph{Correct Question:} The tutor performed extremely well by providing very useful facts. Your answer to the question concerning needs-based financial aid was correct.\\

\noindent \emph{Incorrect Question:} Your answer to the question concerning high school study habits was incorrect.\\

\noindent \emph{Incorrect Question:} Your answer to the question concerning on campus housing was incorrect.\\

\noindent \emph{Incorrect Question:} Your answer to the question concerning student evaluations was incorrect.\\

\noindent \emph{Incorrect Question:} Your answer to the question about students' concerns was incorrect.\\

\subsection{Evaluation Section Instructions}

\noindent \emph{Computer Evaluation:}\\
\noindent Next, tell us about your experience using NAS tutoring. Higher numbers indicates a better experience. The first page asks you to evaluate the NAS Tutoring system. These responses may be used as qualitative data in future publications.\\

\noindent The second page asks you to evaluate researchers with whom you interacted. These answers are strictly for our own benefit, and won't be included in publication. We are the only ones who will see your answers to this section.\\

\noindent \emph{Paper / Pencil Evaluation:}\\
\noindent Next, tell us about your experience using NAS tutoring. Higher numbers indicates a better experience. Now may now open your evaluation packet. The first page asks you to evaluate the NAS Tutoring system. These responses may be used as qualitative data in future publications.\\

\noindent The second page asks you to evaluate researchers with whom you interacted. These answers are strictly for our own benefit, and won't be included in publication. We are the only ones who will see your answers to this section. \emph{Please remember to write your user id on your evaluation packet.}\\

\newpage
\subsection{Consent Form}
See next page for the full form.
\begin{figure*}[!h]
    \centering
    \includegraphics[width=\linewidth]{appendix/consent_form.pdf}
\end{figure*}

\end{document}

### 2016-04-25 design/paper/draft1.tex
Updates from ShareLaTeX

@@
 \usepackage{color}      % For warnings and draft notations
+\usepackage{float}
+
+\graphicspath{ {figures/rGraphs/} }
 
@@
 %
+
 \begin{CCSXML}
@@
 %
+\begin{comment}
 \printccsdesc
+\end{comment}
 
@@
 documented how individuals anthropomorphize technology and exhibit attitudes previously thought to be reserved for person to person interaction\cite{nass1999people}\cite{reeves1996people}.
-In the first study, participants interacted with an intelligent tutoring system and were asked to evaluate the system in one of three conditions: 1) evaluating the system on the same physical computer, 2) evaluating the system on a different but identical computer, or 3) evaluating the system with a paper-and-pencil questionnaire.
+In the first study, participants interacted with an intelligent tutoring system and were asked to evaluate the system in one of three conditions: 1) evaluating the system on the same physical computer, 2) evaluating the system on a different but identical computer, or 3) evaluating the system with a pen-and-paper questionnaire.
 Their results showed that participants rated the intelligent tutoring system on the same computer more positively and more homogeneously than in the other conditions.
@@
 Our study is a theoretical replication that measures the effects of social biases in software engineers.
-Moreover, we want to test whether using a personal machine introduces a stronger social bias than public computers.Therefore, we designed an experiment to answer the following research questions:
+Moreover, we want to test whether using a personal machine introduces a stronger social bias than public computers.Therefore, we designed an experiment to answer the following research questions:\\
 
+\noindent \textbf{\emph{Research Question 1:}} do software developers exhibit the social bias phenomena identified in previous studies?\\
+
+\noindent \textbf{\emph{Research Question 2:}} does a software developer's familiarity with a computing environment affect the social bias phenomena?\\
+
+\begin{comment}
 \begin{enumerate}
     \item{Does programming experience affect the social bias phenomena?}
-    \item{Does a software developer's familiarity with a computer affect the social bias phenomena? } 
+    \item{Does a software developer's familiarity with a computer affect the social bias phenomena?} 
 \end{enumerate}
+\end{comment}
 
-We recreated Nass's intelligent tutor using the details found in the original paper.  Our experiment had two independent variables to test our two research questions:
+We recreated Nass's intelligent tutor using the details found in the original paper. Our experiment has two independent variables to test the two research questions:\\
+\begin{enumerate*}
+    \item{\emph{Evaluation method: Participants either used}}
+
+\end{enumerate*}
+
+\begin{comment}
 \begin{enumerate}
@@
 \end{enumerate}
+\end{comment}
 
@@
 \subsection{Participants}
- We had 26 graduate students in Computer Science at NCSU complete the study between the ages of 22 and 30  with the average age being 25.
+ We had 26 graduate students in Computer Science at NCSU complete the study successfully between the ages of 22 and 30  with the average age being 25.
 16 participants were men, and 10 were women.
@@
 Only 2 participants were Americans, with the rest identifying themselves as international students.
+
+ Three students' data had to be thrown out due to incomplete pen-and-paper evaluations.
+One additional person indicated that they changed their mind and no longer wanted their data used (a check box on the informed consent).
+
  \subsubsection{Participant Recruitment} 20 participants were recruited through the introductory masters class in Software Engineering at NCSU.
@@
 At the study's completion, all participants went through a verbal debriefing with additional information about the study.
-\footnote{We eliminated Nass's original condition of evaluating one computer on another because previous, but unpublished replications do not s
+\footnote{We eliminated Nass's original condition of evaluating one computer on another because previous, but unpublished replications have shown that different computer evaluations may or may not mitigate social biases \cite{gownivaripalli}.}
 
@@
 Participants were placed in one of four conditions as indicated on their consent sheet.
+
 \begin{itemize}
-    \item using and evaluating the tutor on a public computer 
-    \item using the tutor on a public computer with paper-and-pencil evaluation
-    \item using and evaluating the tutor on a personal computer
-    \item using the tutor on a personal computer with paper-and-pencil evaluation
+    \item \textit{condition 1}: using and evaluating the tutor on a public computer 
+    \item \textit{condition 2}: using the tutor on a public computer with pen-and-paper evaluation
+    \item \textit{condition 3}: using and evaluating the tutor on a personal computer
+    \item \textit{condition 4}: using the tutor on a personal computer with pen-and-paper evaluation
 \end{itemize}
+We eliminated Nass's original condition of evaluating one computer on another because previous, but unpublished replications have shown that different computer evaluations may or may not mitigate social biases \cite{gownivaripalli}.
+The consent forms were ordered such that participants would be evenly distributed among the conditions, but this did not happen due to unexpected factors.
+First, the professor handing out the consent forms dropped the stack, which got the papers out of order.
+After getting the forms, a few students asked for their group to be switched so they did not have to leave the classroom.
+Otherwise they would not complete the study.
+Lastly, some people did not follow instructions and go to the correct url, did not fill out the pen-and-paper evaluation forms, or did not want their data analyzed.
+On the second day of experiments, participants were evenly distributed, and we were able to use all of the data.
+The resulting counts in each condition were can be seen in table~\ref{ParticiCount}.
+
+\begin{table}[H]
+\resizebox{\columnwidth}{!}{\begin{tabular}{|c|c|c|c|}
+\hline
+     Condition & Class & Volunteer & total \\
+     \hline
+     Public Comp & 4 & 2 & 6\\
+     Public Pen-Paper & 5 & 1 & 6\\
+     Personal Comp & 9 & 1 & 10\\
+     Personal Pen-Paper & 2 & 2 & 4\\
+\hline
+\end{tabular}}
+\caption{Breakdown of participants in each condition by day.}
+\label{ParticiCount}
+\end{table}
 
@@
 After participants completed the scoring session, they would then be asked to evaluate their experience.
-Finally, participants would be debriefed at the end of the experiment where they wold be told the true intention of the study.
+Finally, participants would be debriefed at the end of the experiment where they wold be told the true intentions of the study, including that the tutor was a mock-up and the "politeness" effect previously documented.
 
 Participants were given the website URL as a part of the informed consent along with a user-name and group number.
-If the participant was in a paper-and-pencil group, they would also be given the final questionnaire with a coversheet that explicitly stated that they were to open it only after completing the scoring session.
+If the participant was in a pen-and-paper group, they would also be given the final questionnaire.
 The questionnaire was sealed so that viewing it had to be intentional.
-This was done to control the amount of time that elapses between the end of the scoring session and the evaluation in both the paper-and-pencil scenario and the computerized questionnaire.
+This was done to control the amount of time that elapses between the end of the scoring session and the evaluation in both the pen-and-paper scenario and the computerized questionnaire.
+The pen-and-paper questionnaire was a print-out of the webpages seen by the other conditions.
 Basic demographic information was collected on the first page including age, race, gender, international status, and programming experience.
@@
     \caption{In the tutoring session, users were asked to indicate their knowledge of a topic using one of three possible answers.}
+    \label{TutorFigure}
 \end{figure}
@@
 Participants were told that the tutoring session had two functions: 1) To gauge existing knowledge to avoid teaching the participant things they already knew, and 2) provide new facts that led to new insights on the subject matter.
-During the session, the participant would see a single fact and they had to indicate how familiar they were with that fact on a 3-point scale: 1 (know very little), 2 (know some), or 3 (know a great deal).
+During the session, the participant would see a single fact, and they had to indicate how familiar they were with that fact on a 3-point scale: 1 (know very little), 2 (know some), or 3 (know a great deal) as seen in figure~\ref{TutorFigure}.
 They were told that they would receive 20 facts out of a total of 1,000 possible facts based on the premise that the more familiar they were with a fact, the less they needed additional information on that topic.
@@
 
-\begin{figure}[!h]
-    \includegraphics[width=\linewidth]{figures/website/06_testing.png}
-    \caption{Descriptive caption}
-\end{figure}
-
 \subsubsection{Testing Session}
-After completing the tutoring session, participants took a test with twelve multiple choice questions, each with five possible answers.
+After completing the tutoring session, participants took a test with twelve multiple choice questions, each with five possible answers as seen in figure~\ref{TestingFigure}.
 They were told that the test represented the breadth of topics covered by the tutor's database, and the questions were chosen randomly from a set of 5,000 possible questions.
-Each question was displayed individually, and a randomly timed animation separated each question to simulate the time to query the database.
-However, this was also a deception.
+Each question was displayed individually, and a timed animation separated each question to simulate the time to query the database.
+This was also a deception.
 All participants received the same questions in the same order.
@@
 \begin{figure}[!h]
-    \includegraphics[width=\linewidth]{figures/website/08_scoring.png}
-    \caption{Descriptive caption}
+    \includegraphics[width=\linewidth]{figures/website/06_testing.png}
+    \caption{A multiple-choice question used in the testing session.}
+    \label{TestingFigure}
 \end{figure}
@@
 These statements were specifically worded to invoke the social cue that the expected feedback should be positive.
-This is the only effort made to elicit a social response.
+Icons were originally present, but removed so that users had to read the text in order to find out if the question was marked correct.
+
+The wording of the feedback was the only effort made to elicit a social response.
 Every other social cue was minimized.
@@
 
+\begin{figure}[!h]
+    \includegraphics[width=\linewidth]{figures/website/08_scoring.png}
+    \caption{The feedback shown to the user.  No visual cues were included to force users to read the text.}
+\end{figure}
 \subsubsection{Evaluation Questionnaire}
@@
 The evaluation questionnaire had two sections; the first evaluated the tutor, while the second evaluated the researchers administering the experiment.
-Depending on which group they were in, they would either be filling out additional pages on the website, or a paper-and-pencil version included in the materials provided to them at the beginning.
-The time between completing the scoring session and beginning the evaluation section should be similar across all groups.
+Depending on which group they were in, they would either be filling out additional pages on the website, or a pen-and-paper version included in the materials provided to them at the beginning.
 The instructions and questions in all cases were identical.
-The paper-and-pencil version was a formatted print out of the web page used in the other condition.
 
@@
     \includegraphics[width=\linewidth]{figures/website/13_eval2.png}
-    \caption{Descriptive caption}
+    \caption{Evaluation of the tutor.}
 \end{figure}
@@
 Instead, the researchers would read the feedback themselves and use it to improve future iterations of the experiment.
-This section's purpose was to be used as a control.
-Theoretically, we would expect politeness to be the same across both paper-and-pencil as well as on the computer since they were specifically told that we would be reading their feedback ourselves.
+This section's purpose was to be used as a control of politeness.
+Theoretically, we would expect politeness to be the same across both pen-and-paper as well as on the computer since they were specifically told that we would be reading their feedback ourselves.
 Additionally, since their answers were not recorded for posterity, we would be the \textit{only} people reading it.
-
-\begin{itemize}
-    \item Screen-shots of the website which participants visited.
-    \item Detailed information about the experimental environment: 
-    \begin{itemize}
-        \item Where the study took place.
-        \item What machines people used.
-        \item How long the study took.
-        \item Explanation of the function of the website used.
-    \end{itemize}
-\end{itemize}
+As a result we can compare the politeness shown to us and compare it to the politeness shown to the computer.
 
 \section{Results}
+From our study design, we define the following four conditions:\\
+\begin{enumerate}
+    \item{PUBPP} Subject used public computer, and pen \& paper for evaluation.
+    \item{PUBCE} Subject used public computer and computer for evaluation.
+    \item{PCPP} Subject used personal computer and pen \& paper for evaluation.
+    \item{PCCE} Subject used personal computer and computer for evaluation.
+\end{enumerate}
 
-\begin{itemize}
-    \item Overall description of what our results were.
-\end{itemize}
+We considered further aggregate conditions such as personal (PCPP and PCCE), public (PUBPP and PUBCE) based on which computer type was used by the subject for the study, and pen \& paper, computer based on which medium was used by the subject to evaluate the computer and human researchers.
+Figure \ref{fig:fourCondAvg} shows the average scores for computer evaluations by each of the nine questions across all four conditions.
+When considering the aggregate groups, figure \ref{fig:pervpub} and \ref{fig:ppvcomp} displays the average scores for computer evaluations by question for personal vs public and computer vs pen \& paper respectively.
 
-\subsection{Analysis}
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{FourCondtionAverageScores}
+\centering
+\caption{Average computer scores by question : all conditions}
+\label{fig:fourCondAvg}
+\end{figure}
 
-\begin{itemize}
-    \item Graph describing the differences between CSC group and Psychology group, along with discussion of that graph.
-    \item Table describing differences between CSC groups and Psych group, with discussion.
-    \item Appropriate statistical tests to describe potential inferences that can be made from the results.
-\end{itemize}
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{ScorebyQuestion_persVpub}
+\centering
+\caption{Average computer scores by question : personal vs public computers}
+\label{fig:pervpub}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{ScorebyQuestion_ppVcomp}
+\centering
+\caption{Average computer scores by question : pen and paper vs computer}
+\label{fig:ppvcomp}
+\end{figure}
+
+To get a better idea of the distribution of the computer evaluation scores over the conditions, figure \ref{fig:compBoxPlot} and \ref{fig:humanBoxPlot} show the box and whisker plots for the computer and human researcher evaluation scores respectively.
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{compBoxPlot}
+\centering
+\caption{Distribution of computer scores over all conditions}
+\label{fig:compBoxPlot}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{humanBoxPlot}
+\centering
+\caption{Distribution of human scores over all conditions}
+\label{fig:humanBoxPlot}
+\end{figure}
+
+To answer our research questions, we conducted two tailed T-tests over 9 different measurements in our data, here displayed in table \ref{table:ttest}. With these
+
+\begin{table*}[t]
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|}
+\hline
+Variable 1 & Variable 2   & P-Value    & Mean: Var 1 & Mean: Var 2 \\
+\hline
+Computer & Pen and Paper (Human)        & 0.16                           & 9.09              & 9.52              \\
+Computer & Pen and Paper (Computer)     & 0.15                           & 7.93              & 7.14              \\
+Personal & Public (Human)               & 0.95                           & 9.27              & 9.24              \\
+Personal & Public (Computer)            & 0.2982                         & 7.35              & 7.87              \\
+Human & Computer                        & $2.01*10^{-6}$ ***                 & 9.26              & 7.63              \\
+Human & Computer Non-Homogenous         & 0.005 **                         & 8.79              & 7.41              \\
+Day 1 & Day 2 (Human)                   & 0.009 **                         & 9.12              & 9.76              \\
+Day 1 & Day 2 (Human) Non-Homogenous    & 0.002 **                         & 8.6               & 9.52              \\
+Day 1 & Day 2 (Comp)                     & 0.9                            & 7.64              & 7.57              \\
+\hline
+\end{tabular}}
+\caption{T-Test Results}
+\label{table:ttest}
+\end{table*}
+
+%Three asterisks indicates significance to an alpha of .001, two asterisks indicates 0.01, and finally a single dot indicates 0.1.
+
+\begin{table}[h]
+\resizebox{\columnwidth}{!}{\begin{tabular}{|c|c|}
+\hline
+Condition    & P-Value\\
+\hline
+Programmer Experience (Computer) & 0.62\\
+Programmer Experience (Human) & 0.1 $\cdot$\\
+Type (Human) &  0.65\\ 
+Type (Computer) & 0.38\\
+\hline
+\end{tabular}}
+\caption{Analysis of Variance Results}
+\label{my-label}
+\end{table}
 
@@
 
-\noindent \textbf{Internal Validity:} \\
+Since our study is a theoretical replication of the original Computers as Social Actors experiment, several new internal and external threats to validity exist.\\
 
-- no non-computer science students run through study / comparing to Nass might not be appropriate given time difference between studies.
+\emph{Internal Validity:} The main limitation of our study is the lack of participants having no software development experience.
+In the seventeen years since the Nass study, common knowledge of computer technology has evolved for individuals without technical education.
+By running the study with both software engineers and individuals with no technical background, potential confounding factors introduced by this evolution would be addressed and the study's findings could be further strengthened.
+Limited access to students outside the computer science department made eliminating this threat impractical within the study's completion time-frame.
 
-- Limited access to potential study participants.
+Access to study participants even within the computer science department was also a challenge given the large number of subjects needed to reach an ideal representative population.
+Consequently, the individuals who did participate might exhibit a self selection bias.
+Nearly all students were not just software developers, but also software engineering graduate students.
+These students might have an inherent interest in our study, potentially artificially motivating their responses.
+Additionally, given their targeted software engineering education, these students might have been able to deduce the purpose of the study during their participation.
+This scenario could also alter their responses.\\
 
-- self selection - participants were not just software developers, but nearly all were also software engineering students.
-
-- As a result of above, they might have been able to figure out what we were doing.
-
-- some students figured out the tutoring system was fake / could have changed their motivation during evaluation session.
-
-\noindent \textbf{External Validity:} \\
-
-- population diversity: age, international status, graduate population vs. professional software developers
-
-- representative sample size: smaller sample size, groups had difference sample sizes
-
-- MCsSE students motivated to complete study because of degree credit requirement
+\emph{External Validity:} The diversity of our population is the primary threat to the generalizability of our results to additional populations.
+The demographics of our population cluster around international computer science graduate students in their early to mid-twenties.
+These individuals are strongly differentiated in level of technical education compared to the general public; however, they still might not faithfully represent software developers as a whole.
+Furthermore, graduate students in the Software Engineering Master's ``Track" receive degree credit for their participation.
+This factor presents a potential artificial motivator that threatens validity; however, we consider this effect to be minimal since several students declined to accept credit when asked.
 
@@
 
-\newpage
+%\newpage
 \appendix
@@
     \includegraphics[width=\linewidth]{appendix/signup_form.png}
+    \caption{The study sign-up form linked to from the recruitment email.}
 \end{figure}
@@
 
-\noindent \emph{Paper / Pencil Evaluation:}\\
+\noindent \emph{Pen / Paper Evaluation:}\\
 \noindent Next, tell us about your experience using NAS tutoring.

### 2016-04-25 paper/draft1.tex
Fixed directory structure.

@@
 \begin{abstract}
-\begin{itemize}
-    \item Standard abstract, defines what we were able to achieve.
-\end{itemize}
+Surveys are a commonly used for assessment purposes in software engineering, but developers are rarely aware of biases inherent in computer-based evaluations.
+In 1999, Nass et al.
+conducted a series of studies which indicated that people exhibit social biases towards computers.
+We conducted a theoretical replication of Nass's original experiment to evaluate these effects in software engineers.
+Our results suggest that a developers' intricate knowledge of computers may diminish or eliminate the behaviors observed in previous experiments with different demographics.
+Furthermore, our experimental design can inform future survey-based experiments that aim to compare the behaviors of software engineers and non-software engineers.
+
+\begin{comment}In 1999, Nass et al.
+conducted a series of studies to establish the presence of normative-response bias and interviewer-based bias in human responses to a computer interviewer agent.
+During the time since the study, computers have become prevalent in society and are an integral component of both personal and professional life.
+In our work, we conduct a theoretical replication of the study by Nass and colleagues to verify whether the results of the study still holds in today's more technologically savvy society.
+We also study the bias in detail among software developers who maintain a collaborative relationship with their computers by comparing their responses with non-software developer participants.
+Our findings show that human social biases regarding interview are still present in responses to computers, and software developers also demonstrate this bias despite the contrary perception that they should not hold such biases given their intricate knowledge of the computer as the interviewer.
+\end{comment}
+
 \end{abstract}
@@
 \section{Introduction}
-\begin{itemize}
-    \item Define what Nass' study was.
-    \item Define what is novel about our study in comparison to Nass' original study.
-    \item Introduce who our subjects are and the basics of what our methodology was.
-\end{itemize}
+In research interviews, honest and forthcoming answers are essential to the process.
+Interviews are plagued by biases inherent in social interactions.
+Such biases include the normative-response bias (people not wanting to admit to answers that are counter to the perceived norm), interviewer-based bias (people answering based on the perceived preference of the interviewer), and politeness norms (people modifying answers to avoid offending).
+Computer systems were introduced to mitigate these known social biases by providing anonymity and an emotionless interviewer.
+Since everyone is aware that computers do not have feelings, it was assumed that the phenomenon would not transfer to human computer interaction.
+
+Through a series of studies, Nass et al.
+documented how individuals anthropomorphize technology and exhibit attitudes previously thought to be reserved for person to person interaction\cite{nass1999people}\cite{reeves1996people}.
+In the first study, participants interacted with an intelligent tutoring system and were asked to evaluate the system in one of three conditions: 1) evaluating the system on the same physical computer, 2) evaluating the system on a different but identical computer, or 3) evaluating the system with a pen-and-paper questionnaire.
+Their results showed that participants rated the intelligent tutoring system on the same computer more positively and more homogeneously than in the other conditions.
+The results suggested that humans unintentionally, unknowingly apply social rules to computer systems.
+
+The way people interact with computers has changed significantly since the study was published  in 1999.
+Computers are now an integral part of both personal and professional life, and users often form strong bonds with their personal devices.
+Software developers are more aware of the inanimate nature of machines, but they likely spend more time in front of a computer than those in other professions.
+Our study is a theoretical replication that measures the effects of social biases in software engineers.
+Moreover, we want to test whether using a personal machine introduces a stronger social bias than public computers.Therefore, we designed an experiment to answer the following research questions:\\
+
+\noindent \textbf{\emph{Research Question 1:}} do software developers exhibit the social bias phenomena identified in previous studies?\\
+
+\noindent \textbf{\emph{Research Question 2:}} does a software developer's familiarity with a computing environment affect the social bias phenomena?\\
+
+\begin{comment}
+\begin{enumerate}
+    \item{Does programming experience affect the social bias phenomena?}
+    \item{Does a software developer's familiarity with a computer affect the social bias phenomena?} 
+\end{enumerate}
+\end{comment}
+
+We recreated Nass's intelligent tutor using the details found in the original paper. Our experiment has two independent variables to test the two research questions:\\
+\begin{enumerate*}
+    \item{\emph{Evaluation method: Participants either used one computer for the entire experiment, or they completed the Evaluation Session on an identical pen-and-paper questionnaire.}}
+\end{enumerate*}
+
+\begin{comment}
+\begin{enumerate}
+    \item {\textit{Evaluation method}: Participants either used one computer for the entire experiment, or they completed the final evaluation on an identical pen-and-paper questionnaire.}
+    \item {\textit{Computing environment}: Participants either used their personal laptops or a public computer in a computer lab.}
+\end{enumerate}
+\end{comment}
 
 \section{Related Work}
+Previous research demonstrates that computers are often treated as social entities despite their inanimate nature.
+Some studies have focused on the human application of social norms and expectations to computers in a seamless manner.
+In addition to the original study, Nass et al.
+performed a series of follow-up experiments that suggest that social stereotypes attributed to gender, ethnicity, and group loyalty, along with deeply ingrained social habits and behaviors like, reciprocity and reciprocal self-disclosure, are extended to computers when interacting with them~\cite{Nass2000machines,nass1999people}.
+Moreover, this behavior is not only limited to computers, human users anthropomorphize other technological mediums like television~\cite{reeves1996people}.
 
 \begin{comment}
-In research interviews open, frank speech is essential to the process.
-Interviews are plagued by biases inherent in social interactions.
-Such biases include the normative-response bias (people not wanting to admit to answers that are counter to the perceived norm), interviewer-based bias (people answering based on the perceived preference of the interviewer), and politeness norms (people modifying answers to avoid offending).
-Computer systems were introduced to mitigate these known social-biases by providing anonymity.
-However, through a series of studies, Nass et al.
-documented how individuals anthropomorphize technology and exhibit attitudes previously thought to be reserved for person to person interaction \cite{nass1999people}\cite{reeves1996people}.
-Contrary to what was believed at the time, the results suggested that humans unintentionally, unknowingly apply social rules to computer systems.
-This foundational work sparked further studies to replicate, validate, and extend this assertion.
-Since the initial set of studies were conducted entirely in the United States, additional research validated the findings across other cultures \cite{katagiri2001cross}.
-Furthermore, the existence of computers as social entities has been studied to better understand racial biases in interviews\cite{krysan2003race}, how the quality of interaction affects expressive systems \cite{vidyarthi2011sympathetic}, and even how to leverage social cues to more effectively sell products online \cite{wang2007can}.
-To our knowledge, no studies currently exist which attempt to replicate these effects with software developers.
-In order to create better software, it is important to study the attitudes of software developers and how they view their work environments.
-Given software developers’ advanced understanding of how computers work, one would expect the attribution of social qualities to computers to be minimal or not present.
-At the same time, it has been shown that humans with accurate mental models are more effective in maintaining teammate bonds with automated computer systems \cite{wilkison2008effects}.
-Given this premise, we are interested in exploring the following questions:
-
-\begin{itemize}
-    \item Do software developers exhibit social-biases towards computers?
-    \item Does ownership1 of the computer modify the exhibited social-biases? 
-\end{itemize}
+The authors concluded that doing the evaluation on a different computer was experimentally equivalent to doing the evaluation with pen-and-paper.
+\footnote{A more recent, but unpublished replication study found that using a different computer resulted in the same effect as using the same computer\cite{gownivaripalli}.}
 \end{comment}
-
-Previous research demonstrates that computers are often treated as social entities despite their inanimate nature.
-There have been studies that focus on the human application of social norms and expectations to computers in a seamless manner.
-Nass et al.
-performed a series of experiments that pointed out that social stereotypes attributed to gender, ethnicity, and group loyalty, along with deeply ingrained social habits and behaviors like, reciprocity and reciprocal self-disclosure, are extended to computers when interacting with them~\cite{Nass2000machines,nass1999people}.
-Moreover, prior studies documented that this behavior is not only limited to computers, human users anthropomorphize other technological mediums like television~\cite{reeves1996people}.
-
-\hfill
 
@@
 
-\hfill
-
 Software developers maintain a collaborative environment with their computers to complete their tasks.
@@
 This type of attribution would be expected, if the the sociability of a computer system is modified by the quality of an individual's mental model of a computer system.
-Research has shown that human-computer team performance is higher when human users have accurate mental models~\cite{wilkison2008effects}.
+Research has shown that human-computer team performance is higher when human users have accurate mental models~\cite{wilkison2007effects}.
 Further studies by Bickmore and Picard have documented the long-term relation establishment and maintenance between a human-computer team by observing that human users of a relational computer agent did not only respect, trust, and like the agent, but also wanted to continue working with the agent even after the end of the study~\cite{Bickmore:2005:EML:1067860.1067867}.
@@
 \subsection{Participants}
-Here we will detail the composition of our study participants including:
+ We had 26 graduate students in Computer Science at NCSU complete the study successfully between the ages of 22 and 30  with the average age being 25.
+16 participants were men, and 10 were women.
+The shortest amount of programming experience was 5 months, and the longest was 10 years with the average being just under 5 years.
+Only 2 participants were Americans, with the rest identifying themselves as international students.
+
+ Three students' data had to be thrown out due to incomplete pen-and-paper evaluations.
+One additional person indicated that they changed their mind and no longer wanted their data used (a check box on the informed consent).
+
+ \subsubsection{Participant Recruitment} 20 participants were recruited through the introductory masters class in Software Engineering at NCSU.
+Students were given the option to leave rather than participate.
+The other 6 participants were emailed through the Software Engineering Master's track and volunteered to come in on a separate day.
+
+ \subsection{Testing Environment}
+ The students recruited from the class all took the experiment at the same time either in the classroom on their laptops, or in a public computer lab down the hall.
+At least one researcher stayed in each room at all times to answer questions.
+
+ The other participants came to the same computer lab that was used with the class and were asked to bring their laptops with them.
+Once they arrived they were either set up at a table with their laptop, or directed to use a public computer.
+No more than two students took the experiment at the same time during this day, and there were always two researchers present at all times.
+
+ All participants were given the same introductory instructions and signed informed-consent forms before beginning the experiment.
+At the study's completion, all participants went through a verbal debriefing with additional information about the study.
+\footnote{We eliminated Nass's original condition of evaluating one computer on another because previous, but unpublished replications have shown that different computer evaluations may or may not mitigate social biases \cite{gownivaripalli}.}
+
+\subsection{Conditions}
+Participants were placed in one of four conditions as indicated on their consent sheet.
+
 \begin{itemize}
-    \item The number in each group
-    \item Programming experience breakdown
-    \item Gender breakdown (potentially)
+    \item \textit{condition 1}: using and evaluating the tutor on a public computer 
+    \item \textit{condition 2}: using the tutor on a public computer with pen-and-paper evaluation
+    \item \textit{condition 3}: using and evaluating the tutor on a personal computer
+    \item \textit{condition 4}: using the tutor on a personal computer with pen-and-paper evaluation
 \end{itemize}
+We eliminated Nass's original condition of evaluating one computer on another because previous, but unpublished replications have shown that different computer evaluations may or may not mitigate social biases \cite{gownivaripalli}.
+The consent forms were ordered such that participants would be evenly distributed among the conditions, but this did not happen due to unexpected factors.
+First, the professor handing out the consent forms dropped the stack, which got the papers out of order.
+After getting the forms, a few students asked for their group to be switched so they did not have to leave the classroom.
+Otherwise they would not complete the study.
+Lastly, some people did not follow instructions and go to the correct url, did not fill out the pen-and-paper evaluation forms, or did not want their data analyzed.
+On the second day of experiments, participants were evenly distributed, and we were able to use all of the data.
+The resulting counts in each condition were can be seen in table~\ref{ParticiCount}.
+
+\begin{table}[H]
+\resizebox{\columnwidth}{!}{\begin{tabular}{|c|c|c|c|}
+\hline
+     Condition & Class & Volunteer & total \\
+     \hline
+     Public Comp & 4 & 2 & 6\\
+     Public Pen-Paper & 5 & 1 & 6\\
+     Personal Comp & 9 & 1 & 10\\
+     Personal Pen-Paper & 2 & 2 & 4\\
+\hline
+\end{tabular}}
+\caption{Breakdown of participants in each condition by day.}
+\label{ParticiCount}
+\end{table}
 
 \subsection{Procedure}
-Generally, here we will detail the procedure by which the study was conducted.
 
-\begin{itemize}
-    \item Screenshots of the website which participants visited.
-    \item Detailed information about the experimental environment: 
-    \begin{itemize}
-        \item Where the study took place.
-        \item What machines people used.
-        \item How long the study took.
-        \item Explaination of the function of the website used.
-    \end{itemize}
-\end{itemize}
+The following procedure is a theoretical replication of the original Nass study.
+Participants were told that they would test and evaluate an artificial tutoring system focused on American college culture.
+The tutor consisted of three parts: a tutorial that gauged existing knowledge as well as offered new knowledge, a testing session, and a scoring session.
+After participants completed the scoring session, they would then be asked to evaluate their experience.
+Finally, participants would be debriefed at the end of the experiment where they wold be told the true intentions of the study, including that the tutor was a mock-up and the "politeness" effect previously documented.
+
+Participants were given the website URL as a part of the informed consent along with a user-name and group number.
+If the participant was in a pen-and-paper group, they would also be given the final questionnaire.
+The questionnaire was sealed so that viewing it had to be intentional.
+This was done to control the amount of time that elapses between the end of the scoring session and the evaluation in both the pen-and-paper scenario and the computerized questionnaire.
+The pen-and-paper questionnaire was a print-out of the webpages seen by the other conditions.
+Basic demographic information was collected on the first page including age, race, gender, international status, and programming experience.
+The tutoring system provided the participants will all the necessary instructions throughout the experiment.
+
+\begin{figure}[!h]
+    \includegraphics[width=\linewidth]{figures/website/04_tutoring.png}
+    \caption{In the tutoring session, users were asked to indicate their knowledge of a topic using one of three possible answers.}
+    \label{TutorFigure}
+\end{figure}
+
+\subsubsection{Tutoring Session}
+Participants were told that the tutoring session had two functions: 1) To gauge existing knowledge to avoid teaching the participant things they already knew, and 2) provide new facts that led to new insights on the subject matter.
+During the session, the participant would see a single fact, and they had to indicate how familiar they were with that fact on a 3-point scale: 1 (know very little), 2 (know some), or 3 (know a great deal) as seen in figure~\ref{TutorFigure}.
+They were told that they would receive 20 facts out of a total of 1,000 possible facts based on the premise that the more familiar they were with a fact, the less they needed additional information on that topic.
+This established the user's active role in the tutoring session to engage the user in a social interaction \cite{nass1993voices}.
+However, this was a deception.
+All participants received the same facts in the same order.
+
+\subsubsection{Testing Session}
+After completing the tutoring session, participants took a test with twelve multiple choice questions, each with five possible answers as seen in figure~\ref{TestingFigure}.
+They were told that the test represented the breadth of topics covered by the tutor's database, and the questions were chosen randomly from a set of 5,000 possible questions.
+Each question was displayed individually, and a timed animation separated each question to simulate the time to query the database.
+This was also a deception.
+All participants received the same questions in the same order.
+
+Some questions were worded so that there was no objectively correct answer.
+For example "What percentage of students usually live on a college campus?"  This answer changes wildly from school to school, and thus there is no correct answer.
+This became very important for the scoring session which was also deceptive.
+
+\begin{figure}[!h]
+    \includegraphics[width=\linewidth]{figures/website/06_testing.png}
+    \caption{A multiple-choice question used in the testing session.}
+    \label{TestingFigure}
+\end{figure}
+
+\subsubsection{Scoring Session}
+The instructions for the scoring session stated that the tutor would evaluate the participants' performance on the test as well as its own performance in preparing them for it.
+Questions were revealed two at a time as being marked correct or incorrect.
+All users were told that they got an eight out of twelve.
+Since all users were told that they  missed the same four questions, correct answers could not be revealed.
+
+Instead of giving the correct answer, the tutor praised its own performance if the user got it right or said that it "underestimated" the user's knowledge if that answer was marked incorrect.
+These statements were specifically worded to invoke the social cue that the expected feedback should be positive.
+Icons were originally present, but removed so that users had to read the text in order to find out if the question was marked correct.
+
+The wording of the feedback was the only effort made to elicit a social response.
+Every other social cue was minimized.
+The tutor was not anthropomorphized in any way.
+It only referred to itself as "the tutor" and never "I".
+No picture or name was given to the tutor, and the language chosen was specifically to exhibit no emotion.
+
+\begin{figure}[!h]
+    \includegraphics[width=\linewidth]{figures/website/08_scoring.png}
+    \caption{The feedback shown to the user.  No visual cues were included to force users to read the text.}
+\end{figure}
+\subsubsection{Evaluation Questionnaire}
+After the participants were done interacting with the tutor, they were asked to evaluate their experience.
+The evaluation questionnaire had two sections; the first evaluated the tutor, while the second evaluated the researchers administering the experiment.
+Depending on which group they were in, they would either be filling out additional pages on the website, or a pen-and-paper version included in the materials provided to them at the beginning.
+The instructions and questions in all cases were identical.
+
+\begin{figure}[!h]
+    \includegraphics[width=\linewidth]{figures/website/12_eval.png}
+    \caption{Descriptive caption}
+\end{figure}
+
+\paragraph{Tutor Evaluation}
+Participants were told that the the answers to these questions would be used as qualitative data in any upcoming publications.
+It was initiated with the statement "For each of the following adjectives, please indicate how well it describes your tutoring experience:" followed by a list of 9 unambiguously positive adjectives.
+Participants answered a 10-point scale from 1 (describes very poorly) to 10 (describes very well) for each word.
+Seven words ("enjoyable", "useful", "informative", "accurate", "analytical", "fun", and "fair") were taken from the original study.
+We also added the words "efficient" and "reliable".
+
+\begin{figure}[!h]
+    \includegraphics[width=\linewidth]{figures/website/13_eval2.png}
+    \caption{Evaluation of the tutor.}
+\end{figure}
+
+\paragraph{Researcher Evaluation}
+The format of the second part of the evaluation was the same as the first.
+Participants were given the same instructions  and a list of new adjectives to describe the researchers with whom they interacted with.
+No adjective appeared in both sections.
+Six of the adjectives ("helpful", "polite", "friendly", "knowledgeable", "competent", "likable") were taking from the original study.
+We added "approachable", "passionate", and "focused".
+
+Participants were told that these answers would not be included in the final paper results.
+Instead, the researchers would read the feedback themselves and use it to improve future iterations of the experiment.
+This section's purpose was to be used as a control of politeness.
+Theoretically, we would expect politeness to be the same across both pen-and-paper as well as on the computer since they were specifically told that we would be reading their feedback ourselves.
+Additionally, since their answers were not recorded for posterity, we would be the \textit{only} people reading it.
+As a result we can compare the politeness shown to us and compare it to the politeness shown to the computer.
 
 \section{Results}
+From our study design, we define the following four conditions:\\
+\begin{enumerate}
+    \item{PUBPP} Subject used public computer, and pen \& paper for evaluation.
+    \item{PUBCE} Subject used public computer and computer for evaluation.
+    \item{PCPP} Subject used personal computer and pen \& paper for evaluation.
+    \item{PCCE} Subject used personal computer and computer for evaluation.
+\end{enumerate}
 
-\begin{itemize}
-    \item Overall description of what our results were.
-\end{itemize}
+We considered further aggregate conditions such as personal (PCPP and PCCE), public (PUBPP and PUBCE) based on which computer type was used by the subject for the study, and pen \& paper, computer based on which medium was used by the subject to evaluate the computer and human researchers.
+Figure \ref{fig:fourCondAvg} shows the average scores for computer evaluations by each of the nine questions across all four conditions.
+When considering the aggregate groups, figure \ref{fig:pervpub} and \ref{fig:ppvcomp} displays the average scores for computer evaluations by question for personal vs public and computer vs pen \& paper respectively.
 
-\subsection{Analysis}
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{FourCondtionAverageScores}
+\centering
+\caption{Average computer scores by question : all conditions}
+\label{fig:fourCondAvg}
+\end{figure}
 
-\begin{itemize}
-    \item Graph describing the differences between CSC group and Psychology group, along with discussion of that graph.
-    \item Table describing differences between CSC groups and Psych group, with discussion.
-    \item Appropriate statistical tests to describe potential inferences that can be made from the results.
-\end{itemize}
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{ScorebyQuestion_persVpub}
+\centering
+\caption{Average computer scores by question : personal vs public computers}
+\label{fig:pervpub}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{ScorebyQuestion_ppVcomp}
+\centering
+\caption{Average computer scores by question : pen and paper vs computer}
+\label{fig:ppvcomp}
+\end{figure}
+
+To get a better idea of the distribution of the computer evaluation scores over the conditions, figure \ref{fig:compBoxPlot} and \ref{fig:humanBoxPlot} show the box and whisker plots for the computer and human researcher evaluation scores respectively.
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{compBoxPlot}
+\centering
+\caption{Distribution of computer scores over all conditions}
+\label{fig:compBoxPlot}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{humanBoxPlot}
+\centering
+\caption{Distribution of human scores over all conditions}
+\label{fig:humanBoxPlot}
+\end{figure}
+
+To answer our research questions, we conducted two tailed T-tests over 9 different measurements in our data, here displayed in table \ref{table:ttest}. With these
+
+\begin{table*}[t]
+\resizebox{\textwidth}{!}{\begin{tabular}{|c|c|c|c|c|}
+\hline
+Variable 1 & Variable 2   & P-Value    & Mean: Var 1 & Mean: Var 2 \\
+\hline
+Computer & Pen and Paper (Human)        & 0.16                           & 9.09              & 9.52              \\
+Computer & Pen and Paper (Computer)     & 0.15                           & 7.93              & 7.14              \\
+Personal & Public (Human)               & 0.95                           & 9.27              & 9.24              \\
+Personal & Public (Computer)            & 0.2982                         & 7.35              & 7.87              \\
+Human & Computer                        & $2.01*10^{-6}$ ***                 & 9.26              & 7.63              \\
+Human & Computer Non-Homogenous         & 0.005 **                         & 8.79              & 7.41              \\
+Day 1 & Day 2 (Human)                   & 0.009 **                         & 9.12              & 9.76              \\
+Day 1 & Day 2 (Human) Non-Homogenous    & 0.002 **                         & 8.6               & 9.52              \\
+Day 1 & Day 2 (Comp)                     & 0.9                            & 7.64              & 7.57              \\
+\hline
+\end{tabular}}
+\caption{T-Test Results}
+\label{table:ttest}
+\end{table*}
+
+%Three asterisks indicates significance to an alpha of .001, two asterisks indicates 0.01, and finally a single dot indicates 0.1.
+
+\begin{table}[h]
+\resizebox{\columnwidth}{!}{\begin{tabular}{|c|c|}
+\hline
+Condition    & P-Value\\
+\hline
+Programmer Experience (Computer) & 0.62\\
+Programmer Experience (Human) & 0.1 $\cdot$\\
+Type (Human) &  0.65\\ 
+Type (Computer) & 0.38\\
+\hline
+\end{tabular}}
+\caption{Analysis of Variance Results}
+\label{my-label}
+\end{table}
 
@@
 
-\subsection{Threats to Validity}
+\subsection{Threats}
 
-\subsubsection{Internal Validity}
+Since our study is a theoretical replication of the original Computers as Social Actors experiment, several new internal and external threats to validity exist.\\
 
-\begin{itemize}
-    \item Describe the mistakes we made.
-\end{itemize}
+\emph{Internal Validity:} The main limitation of our study is the lack of participants having no software development experience.
+In the seventeen years since the Nass study, common knowledge of computer technology has evolved for individuals without technical education.
+By running the study with both software engineers and individuals with no technical background, potential confounding factors introduced by this evolution would be addressed and the study's findings could be further strengthened.
+Limited access to students outside the computer science department made eliminating this threat impractical within the study's completion time-frame.
 
-\subsubsection{External Validity}
+Access to study participants even within the computer science department was also a challenge given the large number of subjects needed to reach an ideal representative population.
+Consequently, the individuals who did participate might exhibit a self selection bias.
+Nearly all students were not just software developers, but also software engineering graduate students.
+These students might have an inherent interest in our study, potentially artificially motivating their responses.
+Additionally, given their targeted software engineering education, these students might have been able to deduce the purpose of the study during their participation.
+This scenario could also alter their responses.\\
 
-\begin{itemize}
-    \item Describe whether our results are significant enough to generalize to future studies.
-\end{itemize}
+\emph{External Validity:} The diversity of our population is the primary threat to the generalizability of our results to additional populations.
+The demographics of our population cluster around international computer science graduate students in their early to mid-twenties.
+These individuals are strongly differentiated in level of technical education compared to the general public; however, they still might not faithfully represent software developers as a whole.
+Furthermore, graduate students in the Software Engineering Master's ``Track" receive degree credit for their participation.
+This factor presents a potential artificial motivator that threatens validity; however, we consider this effect to be minimal since several students declined to accept credit when asked.
 
@@
 \begin{itemize}
-    \item Short brief review of the entire work and it's implications if any.
+    \item Short brief review of the entire work and its implications if any.
 \end{itemize}
@@
 \section*{Acknowledgements}
-We would like to thank...
+We wish to thank Dr.
+Tim Menzies for allowing us to conduct our study with students taking his graduate level software engineering course.
+We also thank CSC710 students for their helpful feedback during the peer review process.
 
@@
 
+%\newpage
 \appendix
-\section{Website and Survey Transcripts}
+
+\section{Transcripts}
+
+\subsection{Recruitment Email and Sign-Up Form}
+
+\noindent Be part of the future of software engineering!
+Students in the CSC710 software engineering course are seeking participants for a research study.
+The study is being conducted on centennial campus, requires 15 to 20 minutes of your time, and counts towards the MCs Software Engineering track participation requirement.
+Click here to sign up today!\\
+
+\noindent Thank you for your interest in participating in our study!
+To be included, please fill out the short form below.
+Once your response is recorded, we will be in touch through the provided email to schedule a date and time for your participation.
+
+\begin{figure}[!h]
+    \centering
+    \includegraphics[width=\linewidth]{appendix/signup_form.png}
+    \caption{The study sign-up form linked to from the recruitment email.}
+\end{figure}
+
+\subsection{Participant Introduction Script}
+
+\noindent Thank you for participating in our study today (for Dr.
+Menzies course: ``Thank you Dr.
+Menzies for having us").
+First, you will be provided a consent form, which describes the details of the study and how participating might affect you.
+Please fill out the consent form and then open the link at the bottom of the form in a web browser.
+You may choose to not participate in the study now or at any point during the study.\\
+
+\noindent Please use the Google Chrome browser if it is available.
+Also, make sure to type in the entire link provided on the consent form.
+Our study uses a product called, NAS Tutoring.
+Once the site is loaded in your browser, you will follow a series of prompts.
+You will be given a user ID on the third page.
+Please make sure to write that ID on the consent form (not your NC State Unity ID).\\
+
+\noindent If you have any questions or problems, please raise your hand and a researcher will help you.
+Finally, please do not hit the back button.
+If you happen to do so, let a researcher know and we can recover your session using your user ID.
+
+\subsection{Participant Debrief Script}
+
+\noindent Thank you for taking the time to complete our study.
+We led you to believe you were using and evaluating a real tutoring system, but this actually isn't the case!
+We created the tutoring system as a way to study and measure software engineer's attitudes toward computers.\\
+
+\noindent Previous studies have shown that, strangely enough, people attribute human qualities to computers and even behave politely towards them as a consequence.
+The facts shown in the tutoring session are true, but the testing session was completely staged.
+Everyone received the same questions and the same four questions were marked incorrect!
+The evaluation session is the only section of the website where your data was recorded.
+We had you evaluate both the tutoring system and the researchers so we can understand the differences in your responses and determine if any significant difference exists.
+
+\subsection{Website Welcome Instructions}
+\noindent Today, you will be working with the NAS Tutoring System.
+This system is designed to help you learn information.
+First, you will be provided with a fact.
+After reading the fact, you should use the mouse to indicate how familiar you are with that particular fact.
+The system then selects the next fact, based on your level of familiarity with the previous fact.
+The more you know about the topic associated with a fact, the less likely you will be to receive additional facts on that topic.\\
+
+\noindent You will receive a total of \emph{20 facts}, chosen from a list \emph{of 1,000 possible facts}.
+After completing the tutoring session, you will take a test.
+The test will involve 12 multiple-choice questions, randomly chosen from a set of 5,000 questions.
+The system will then evaluate your performance on the test and evaluate its own performance as a tutor.
+
+\subsection{Tutoring Session Facts}
+\noindent Fact 1: 76\% of students get into their first choice college\\[\baselineskip]
+\noindent Fact 2: 75\% of the colleges and universities in the U.S. are East of the Mississippi River\\[\baselineskip]
+\noindent Fact 3: Being an athlete increases your chances of being accepted to college.\\[\baselineskip]
+\noindent Fact 4: 46.5\% of high school students frequently or occasionally fell asleep in class during their senior year.\\[\baselineskip]
+\noindent Fact 5: Tuition increases for those who can pay full price, subsidizing the cost for those who cannot.\\[\baselineskip]
+\noindent Fact 6: 42\% of freshmen expect to earn a master's degree.\\[\baselineskip]
+\noindent Fact 7: Less than 5\% of American families have saved enough for college.\\[\baselineskip]
+\noindent Fact 8: Students who need financial aid are not guaranteed to receive it.\\[\baselineskip]
+\noindent Fact 9: 53\% of all international students in the U.S. come from China, Canada, India, Taiwan, South Korea and Japan.\\[\baselineskip]
+\noindent Fact 10: Early admission applicants are typically NOT stronger or more qualified than other applicants.\\[\baselineskip]
+\noindent Fact 11: Two-thirds of all college students get some form of financial aid.\\[\baselineskip]
+\noindent Fact 12: U.S. colleges do not require students to declare majors upon admission.\\[\baselineskip]
+\noindent Fact 13: Students do not need to receive a high school diploma in order to go to college.\\[\baselineskip]
+\noindent Fact 14: U.S. colleges have a higher workload than most U.S. high schools.\\[\baselineskip]
+\noindent Fact 15: The term \"Ivy League\" is used to describe a college athletic conference.\\[\baselineskip]
+\noindent Fact 16: Only 14\% of freshman attend college 500 or more miles away.\\[\baselineskip]
+\noindent Fact 17: 50\% of college freshman earned a grade point average equal to or greater than an A- in high school.\\[\baselineskip]
+\noindent Fact 18: 55\% of high school students took at least one AP class and 21.7\% took at least five AP courses."\\[\baselineskip]
+\noindent Fact 19: Only 18.2\% of college students said national magazine college rankings were ``very important" in their decision to attend their chosen school.\\[\baselineskip]
+\noindent Fact 20: 85\% of students attending private colleges are awarded merit aid.
+
+\subsection{Testing Session Questions}
+\noindent Question 1: A majority of international students apply to college in which state?\\[\baselineskip]
+\noindent Question 2: What percentage of a school's financial aid budget goes to affluent students?\\[\baselineskip]
+\noindent Question 3: International students comprise what percentage of the graduating class of 2015?\\[\baselineskip]
+\noindent Question 4: A majority of students attend college no more than how many miles away from their home town?\\[\baselineskip]
+\noindent Question 5: How many hours a week do high school students spend studying?\\[\baselineskip]
+\noindent Question 6: What percentage of students report that they felt overwhelmed at college?\\[\baselineskip]
+\noindent Question 7: In which subject did a quarter of college freshmen say they needed tutoring?\\[\baselineskip]
+\noindent Question 8: What percentage of high school seniors reported that they did not read a book for fun?\\[\baselineskip]
+\noindent Question 9: What percentage of students live on campus?\\[\baselineskip]
+\noindent Question 10: What percentage of students rated themselves as being above average in their academic ability?\\[\baselineskip]
+\noindent Question 11: How concerned are college freshmen about paying back student loans?\\[\baselineskip]
+\noindent Question 12: How high can a family's income be before they are ineligible for needs-based financial aid?\\
+
+\subsection{Scoring Session Feedback}
+\noindent The website displayed the following text as scoring feedback:\\
+
+\noindent \emph{Correct Question:} The tutor performed extremely well by providing very useful facts. Your answer to the question concerning needs-based financial aid was correct.\\
+
+\noindent \emph{Incorrect Question:} Your answer to the question concerning high school study habits was incorrect.\\
+
+\noindent \emph{Incorrect Question:} Your answer to the question concerning on campus housing was incorrect.\\
+
+\noindent \emph{Incorrect Question:} Your answer to the question concerning student evaluations was incorrect.\\
+
+\noindent \emph{Incorrect Question:} Your answer to the question about students' concerns was incorrect.\\
+
+\subsection{Evaluation Section Instructions}
+
+\noindent \emph{Computer Evaluation:}\\
+\noindent Next, tell us about your experience using NAS tutoring.
+Higher numbers indicates a better experience.
+The first page asks you to evaluate the NAS Tutoring system.
+These responses may be used as qualitative data in future publications.\\
+
+\noindent The second page asks you to evaluate researchers with whom you interacted.
+These answers are strictly for our own benefit, and won't be included in publication.
+We are the only ones who will see your answers to this section.\\
+
+\noindent \emph{Pen / Paper Evaluation:}\\
+\noindent Next, tell us about your experience using NAS tutoring.
+Higher numbers indicates a better experience.
+Now may now open your evaluation packet.
+The first page asks you to evaluate the NAS Tutoring system.
+These responses may be used as qualitative data in future publications.\\
+
+\noindent The second page asks you to evaluate researchers with whom you interacted.
+These answers are strictly for our own benefit, and won't be included in publication.
+We are the only ones who will see your answers to this section.
+\emph{Please remember to write your user id on your evaluation packet.}\\
+
+\newpage
+\subsection{Consent Form}
+See next page for the full form.
+\begin{figure*}[!h]
+    \centering
+    \includegraphics[width=\linewidth]{appendix/consent_form.pdf}
+\end{figure*}
 

### 2016-04-25 paper/finalSubmission.tex
Fixed directory structure.

--- 2016-04-24 design/paper/draft1.tex
@@
 \begin{abstract}
-Surveys are a commonly used for assessment purposes in software engineering, but developers are rarely aware of biases inherent in computer-based evaluations.
+In order to effectively evaluate their work, software developers need to be aware of biases inherent in computer evaluations.
 In 1999, Nass et al.
-conducted a series of studies which indicated that people exhibit social biases towards computers.
-We conducted a theoretical replication of Nass's original experiment to evaluate these effects in software engineers.
-Our results suggest that a developers' intricate knowledge of computers may diminish or eliminate the behaviors observed in previous experiments with different demographics.
-Furthermore, our experimental design can inform future survey-based experiments that aim to compare the behaviors of software engineers and non-software engineers.
-
-\begin{comment}In 1999, Nass et al.
-conducted a series of studies to establish the presence of normative-response bias and interviewer-based bias in human responses to a computer interviewer agent.
-During the time since the study, computers have become prevalent in society and are an integral component of both personal and professional life.
-In our work, we conduct a theoretical replication of the study by Nass and colleagues to verify whether the results of the study still holds in today's more technologically savvy society.
-We also study the bias in detail among software developers who maintain a collaborative relationship with their computers by comparing their responses with non-software developer participants.
-Our findings show that human social biases regarding interview are still present in responses to computers, and software developers also demonstrate this bias despite the contrary perception that they should not hold such biases given their intricate knowledge of the computer as the interviewer.
-\end{comment}
-
+conducted a series of studies showing that people exhibited social biases (politeness) when completing computer-based evaluation surveys in the same way as if the survey was conducted by a person.
+We conducted a theoretical replication of Nass's original experiment that implies that software developer's intricate knowledge of the computers may diminish or eliminate behaviors previously documented in other demographics.
+These results can inform survey-based experimental design that compares software engineers to non-software engineers.
 \end{abstract}
@@
 \section{Introduction}
-In research interviews, honest and forthcoming answers are essential to the process.
+In research interviews open, frank speech is essential to the process.
 Interviews are plagued by biases inherent in social interactions.
 Such biases include the normative-response bias (people not wanting to admit to answers that are counter to the perceived norm), interviewer-based bias (people answering based on the perceived preference of the interviewer), and politeness norms (people modifying answers to avoid offending).
-Computer systems were introduced to mitigate these known social biases by providing anonymity and an emotionless interviewer.
-Since everyone is aware that computers do not have feelings, it was assumed that the phenomenon would not transfer to human computer interaction.
+Logically, everyone knows that computers do not have feelings, so it was assumed that the phenomenon would not transfer to human computer interaction.
 
-Through a series of studies, Nass et al.
+Computer systems were introduced to mitigate these known social biases by providing anonymity.
+However, through a series of studies, Nass et al.
 documented how individuals anthropomorphize technology and exhibit attitudes previously thought to be reserved for person to person interaction\cite{nass1999people}\cite{reeves1996people}.
+Contrary to what was believed at the time, the results suggested that humans unintentionally, unknowingly apply social rules to computer systems.
 In the first study, participants interacted with an intelligent tutoring system and were asked to evaluate the system in one of three conditions: 1) evaluating the system on the same physical computer, 2) evaluating the system on a different but identical computer, or 3) evaluating the system with a paper-and-pencil questionnaire.
 Their results showed that participants rated the intelligent tutoring system on the same computer more positively and more homogeneously than in the other conditions.
-The results suggested that humans unintentionally, unknowingly apply social rules to computer systems.
+The authors concluded that doing the evaluation on a different computer was experimentally equivalent to doing the evaluation with pen-and-paper.
+However, more recent replication studies have found the opposite to be true\cite{gownivaripalli}.
 
@@
 Computers are now an integral part of both personal and professional life, and users often form strong bonds with their personal devices.
-Software developers are more aware of the inanimate nature of machines, but they likely spend more time in front of a computer than those in other professions.
-Our study is a theoretical replication that measures the effects of social biases in software engineers.
-Moreover, we want to test whether using a personal machine introduces a stronger social bias than public computers.Therefore, we designed an experiment to answer the following research questions:
+Our study is a theoretical replication that has been updated to test whether using a personal machine introduces a stronger social bias than public computers.
+Moreover, we want to test whether familiarity with programming changes this bias.
+Software developers are more aware of the inanimate nature of machines, but they also likely spend more time in front of a computer than other professions.
+Therefore, we designed an experiment to answer the following research questions:
 
@@
 
-We recreated Nass's intelligent tutor using the details found in the original paper.  Our experiment had two independent variables to test our two research questions:
-\begin{enumerate}
-    \item {\textit{Evaluation method}: Participants either used one computer for the entire experiment, or they completed the final evaluation on an identical pen-and-paper questionnaire.}
-    \item {\textit{Computing environment}: Participants either used their personal laptops or a public computer in a computer lab.}
-\end{enumerate}
+ We recreated Nass's intelligent tutor experiment using the details found in the original paper.
+Participants evaluated the tutor on either the same machine, or filled out an identical pen-and-paper questionnaire.
+We targeted exclusively software engineers to complete the experiment either on their personal laptops or in a public computer lab.
 
@@
 Previous research demonstrates that computers are often treated as social entities despite their inanimate nature.
-Some studies have focused on the human application of social norms and expectations to computers in a seamless manner.
-In addition to the original study, Nass et al.
-performed a series of follow-up experiments that suggest that social stereotypes attributed to gender, ethnicity, and group loyalty, along with deeply ingrained social habits and behaviors like, reciprocity and reciprocal self-disclosure, are extended to computers when interacting with them~\cite{Nass2000machines,nass1999people}.
-Moreover, this behavior is not only limited to computers, human users anthropomorphize other technological mediums like television~\cite{reeves1996people}.
-
-\begin{comment}
-The authors concluded that doing the evaluation on a different computer was experimentally equivalent to doing the evaluation with pen-and-paper.
-\footnote{A more recent, but unpublished replication study found that using a different computer resulted in the same effect as using the same computer\cite{gownivaripalli}.}
-\end{comment}
+There have been studies that focus on the human application of social norms and expectations to computers in a seamless manner.
+Nass et al.
+performed a series of experiments that pointed out that social stereotypes attributed to gender, ethnicity, and group loyalty, along with deeply ingrained social habits and behaviors like, reciprocity and reciprocal self-disclosure, are extended to computers when interacting with them~\cite{Nass2000machines,nass1999people}.
+Moreover, prior studies documented that this behavior is not only limited to computers, human users anthropomorphize other technological mediums like television~\cite{reeves1996people}.
 
@@
 \subsection{Participants}
- We had 26 graduate students in Computer Science at NCSU complete the study between the ages of 22 and 30  with the average age being 25.
-16 participants were men, and 10 were women.
-The shortest amount of programming experience was 5 months, and the longest was 10 years with the average being just under 5 years.
-Only 2 participants were Americans, with the rest identifying themselves as international students.
- \subsubsection{Participant Recruitment} 20 participants were recruited through the introductory masters class in Software Engineering at NCSU.
-Students were given the option to leave rather than participate.
-The other 6 participants were emailed through the Software Engineering Master's track and volunteered to come in on a separate day.
+We designed the study to include 60 participants: 20 psychology undergrads, and 40 students in the software development masters program.
+The masters students were given credit for participating in the study as a part of a requirement for their degree.
+The Psychology students were given extra credit in a class for participating.\footnote{Incentives from the Psychology professor are subject to change until the point when the experiment is complete.}  Participants were told beforehand that the experiment involved the use of a computer tutor.
+All participants signed informed consent forms and were given additional information in a debriefing at the study's completion.
 
- \subsection{Testing Environment}
- The students recruited from the class all took the experiment at the same time either in the classroom on their laptops, or in a public computer lab down the hall.
-At least one researcher stayed in each room at all times to answer questions.
+Next paragraph to be completed after study is complete with final demographic information.
+Here we will detail the composition of our study participants including:
+\begin{itemize}
+    \item The number in each group
+    \item Programming experience breakdown
+    \item Gender breakdown (potentially)
+\end{itemize}
 
- The other participants came to the same computer lab that was used with the class and were asked to bring their laptops with them.
-Once they arrived they were either set up at a table with their laptop, or directed to use a public computer.
-No more than two students took the experiment at the same time during this day, and there were always two researchers present at all times.
+Participants were evenly distributed between six different conditions in our subjects experimental design\footnote{The original Nass study did not target participants in software engineering.
+As a result, the original findings should be comparable to non-software engineering students evaluating a public computer.}:
+\begin{itemize}
+    \item non-software engineering students evaluating personal computer on the same  computer
+    \item non-software engineering students evaluating personal computer with paper-and-pencil
+    \item software engineering students evaluating public computer on the same computer
+    \item software engineering students evaluating public computer with paper-and-pencil
+    \item software engineering students evaluating personal computer on the same computer
+    \item software engineering students evaluating personal computer with paper-and-pencil
+\end{itemize}
 
- All participants were given the same introductory instructions and signed informed-consent forms before beginning the experiment.
-At the study's completion, all participants went through a verbal debriefing with additional information about the study.
-\footnote{We eliminated Nass's original condition of evaluating one computer on another because previous, but unpublished replications do not s
-
-\subsection{Conditions}
-Participants were placed in one of four conditions as indicated on their consent sheet.    
-\begin{itemize}
-    \item using and evaluating the tutor on a public computer 
-    \item using the tutor on a public computer with paper-and-pencil evaluation
-    \item using and evaluating the tutor on a personal computer
-    \item using the tutor on a personal computer with paper-and-pencil evaluation
-\end{itemize}
+\paragraph{Testing environment}
+Will be filled later after the participants have responded.
 
@@
 
-\subsection{Threats}
+\subsection{Threats to Validity}
 
-\noindent \textbf{Internal Validity:} \\
+\subsubsection{Internal Validity}
 
-- no non-computer science students run through study / comparing to Nass might not be appropriate given time difference between studies.
+\begin{itemize}
+    \item Describe the mistakes we made.
+\end{itemize}
 
-- Limited access to potential study participants.
+\subsubsection{External Validity}
 
-- self selection - participants were not just software developers, but nearly all were also software engineering students.
-
-- As a result of above, they might have been able to figure out what we were doing.
-
-- some students figured out the tutoring system was fake / could have changed their motivation during evaluation session.
-
-\noindent \textbf{External Validity:} \\
-
-- population diversity: age, international status, graduate population vs. professional software developers
-
-- representative sample size: smaller sample size, groups had difference sample sizes
-
-- MCsSE students motivated to complete study because of degree credit requirement
+\begin{itemize}
+    \item Describe whether our results are significant enough to generalize to future studies.
+\end{itemize}
 
@@
 \begin{itemize}
-    \item Short brief review of the entire work and its implications if any.
+    \item Short brief review of the entire work and it's implications if any.
 \end{itemize}
@@
 \noindent Fact 19: Only 18.2\% of college students said national magazine college rankings were ``very important" in their decision to attend their chosen school.\\[\baselineskip]
-\noindent Fact 20: 85\% of students attending private colleges are awarded merit aid.
+\noindent Fact 20: 85\% of students attending private colleges are awarded merit aid.\\[\baselineskip]
 
@@
 \noindent Question 11: How concerned are college freshmen about paying back student loans?\\[\baselineskip]
-\noindent Question 12: How high can a family's income be before they are ineligible for needs-based financial aid?\\
+\noindent Question 12: How high can a family's income be before they are ineligible for needs-based financial aid?\\[\baselineskip]
 
 \subsection{Scoring Session Feedback}
-\noindent The website displayed the following text as scoring feedback:\\
-
-\noindent \emph{Correct Question:} The tutor performed extremely well by providing very useful facts. Your answer to the question concerning needs-based financial aid was correct.\\
-
-\noindent \emph{Incorrect Question:} Your answer to the question concerning high school study habits was incorrect.\\
-
-\noindent \emph{Incorrect Question:} Your answer to the question concerning on campus housing was incorrect.\\
-
-\noindent \emph{Incorrect Question:} Your answer to the question concerning student evaluations was incorrect.\\
-
-\noindent \emph{Incorrect Question:} Your answer to the question about students' concerns was incorrect.\\
-
-\subsection{Evaluation Section Instructions}
-
-\noindent \emph{Computer Evaluation:}\\
-\noindent Next, tell us about your experience using NAS tutoring.
-Higher numbers indicates a better experience.
-The first page asks you to evaluate the NAS Tutoring system.
-These responses may be used as qualitative data in future publications.\\
-
-\noindent The second page asks you to evaluate researchers with whom you interacted.
-These answers are strictly for our own benefit, and won't be included in publication.
-We are the only ones who will see your answers to this section.\\
-
-\noindent \emph{Paper / Pencil Evaluation:}\\
-\noindent Next, tell us about your experience using NAS tutoring.
-Higher numbers indicates a better experience.
-Now may now open your evaluation packet.
-The first page asks you to evaluate the NAS Tutoring system.
-These responses may be used as qualitative data in future publications.\\
-
-\noindent The second page asks you to evaluate researchers with whom you interacted.
-These answers are strictly for our own benefit, and won't be included in publication.
-We are the only ones who will see your answers to this section.
-\emph{Please remember to write your user id on your evaluation packet.}\\
 
@@
 \subsection{Consent Form}
-See next page for the full form.
+See next page.
 \begin{figure*}[!h]

### 2016-04-25 paper/draft1.tex
Updates from ShareLaTeX

@@
 
-We recreated Nass's intelligent tutor using the details found in the original paper. Our experiment has two independent variables to test the two research questions:\\
-\begin{enumerate*}
-    \item{\emph{Evaluation method: Participants either used one computer for the entire experiment, or they completed the Evaluation Session on an identical pen-and-paper questionnaire.}}
-\end{enumerate*}
+We recreated Nass's intelligent tutor using the details found in the original paper. Our experiment has two independent variables to test the two research questions:
+\begin{enumerate}
+    \item{\emph{Evaluation method:} Participants either used one computer for the entire experiment, or they completed the Evaluation Session on an identical pen-and-paper questionnaire.}
+    \item {\textit{Computing environment}: Participants either used their personal laptops or a public computer in a computer lab.}
+\end{enumerate}
 
@@
     \item {\textit{Evaluation method}: Participants either used one computer for the entire experiment, or they completed the final evaluation on an identical pen-and-paper questionnaire.}
-    \item {\textit{Computing environment}: Participants either used their personal laptops or a public computer in a computer lab.}
+    \item {\textit{Computing environment}: Participants either used personal laptops or a public computer in a computer lab.}
 \end{enumerate}

### 2016-04-25 paper/draft1.tex
Added tentative results section.

@@
 \begin{abstract}
+
+Previous literature indicates individuals exhibit social biases towards computers; however, it is unknown how a person's level of technical education affects this behavior.
+We conducted a theoretical replication of Nass' computers as social actors experiment which suggests that software engineers do not exhibit the same biases as non-technical individuals.
+By studying how software developers differ from others, we gain a deeper understanding of how biases may shape developers' attitudes towards software.
+Our findings can inform how future survey-based experiments are interpreted in a modern computing environment.
+
+\begin{comment}
 Surveys are a commonly used for assessment purposes in software engineering, but developers are rarely aware of biases inherent in computer-based evaluations.
-In 1999, Nass et al.
-conducted a series of studies which indicated that people exhibit social biases towards computers.
-We conducted a theoretical replication of Nass's original experiment to evaluate these effects in software engineers.
-Our results suggest that a developers' intricate knowledge of computers may diminish or eliminate the behaviors observed in previous experiments with different demographics.
-Furthermore, our experimental design can inform future survey-based experiments that aim to compare the behaviors of software engineers and non-software engineers.
 
-\begin{comment}In 1999, Nass et al.
-conducted a series of studies to establish the presence of normative-response bias and interviewer-based bias in human responses to a computer interviewer agent.
+In 1999, Nass et al. conducted a series of studies to establish the presence of normative-response bias and interviewer-based bias in human responses to a computer interviewer agent.
+
 During the time since the study, computers have become prevalent in society and are an integral component of both personal and professional life.
+
 In our work, we conduct a theoretical replication of the study by Nass and colleagues to verify whether the results of the study still holds in today's more technologically savvy society.
+
 We also study the bias in detail among software developers who maintain a collaborative relationship with their computers by comparing their responses with non-software developer participants.
+
 Our findings show that human social biases regarding interview are still present in responses to computers, and software developers also demonstrate this bias despite the contrary perception that they should not hold such biases given their intricate knowledge of the computer as the interviewer.
@@
 \begin{enumerate}
-    \item{\emph{Evaluation method:} Participants either used one computer for the entire experiment, or they completed the Evaluation Session on an identical pen-and-paper questionnaire.}
-    \item {\textit{Computing environment}: Participants either used their personal laptops or a public computer in a computer lab.}
+    \item{\emph{Evaluation method:} Participants either used one computer for the entire experiment, or they completed the Evaluation Session using an identical pen-and-paper questionnaire.}
+    \item {\textit{Computing environment}: Participants either used personal laptops or a public computer in a computer lab.}
 \end{enumerate}
@@
  Three students' data had to be thrown out due to incomplete pen-and-paper evaluations.
-One additional person indicated that they changed their mind and no longer wanted their data used (a check box on the informed consent).
+One additional person indicated that they changed their mind and no longer wanted their data used (a check box on the informed consent).\\
 
@@
 \begin{itemize}
-    \item \textit{condition 1}: using and evaluating the tutor on a public computer 
-    \item \textit{condition 2}: using the tutor on a public computer with pen-and-paper evaluation
-    \item \textit{condition 3}: using and evaluating the tutor on a personal computer
-    \item \textit{condition 4}: using the tutor on a personal computer with pen-and-paper evaluation
+    \item \textit{PUBCE}: using and evaluating the tutor on a public computer 
+    \item \textit{PUBPP}: using the tutor on a public computer with pen-and-paper evaluation
+    \item \textit{PCCE}: using and evaluating the tutor on a personal computer
+    \item \textit{PCPP}: using the tutor on a personal computer with pen-and-paper evaluation
 \end{itemize}
@@
 \hline
-     Condition & Class & Volunteer & total \\
+     Condition & Class & Volunteer & Total \\
      \hline
-     Public Comp & 4 & 2 & 6\\
+     Public Computer & 4 & 2 & 6\\
      Public Pen-Paper & 5 & 1 & 6\\
-     Personal Comp & 9 & 1 & 10\\
+     Personal Computer & 9 & 1 & 10\\
      Personal Pen-Paper & 2 & 2 & 4\\
@@
 Participants were told that the tutoring session had two functions: 1) To gauge existing knowledge to avoid teaching the participant things they already knew, and 2) provide new facts that led to new insights on the subject matter.
-During the session, the participant would see a single fact, and they had to indicate how familiar they were with that fact on a 3-point scale: 1 (know very little), 2 (know some), or 3 (know a great deal) as seen in figure~\ref{TutorFigure}.
+During the session, the participant would see a single fact, and they had to indicate how familiar they were with that fact on a 3-point scale: 1 (know very little), 2 (know some), or 3 (know a great deal) as seen in Figure~\ref{TutorFigure}.
 They were told that they would receive 20 facts out of a total of 1,000 possible facts based on the premise that the more familiar they were with a fact, the less they needed additional information on that topic.
@@
 \subsubsection{Testing Session}
-After completing the tutoring session, participants took a test with twelve multiple choice questions, each with five possible answers as seen in figure~\ref{TestingFigure}.
+After completing the tutoring session, participants took a test with twelve multiple choice questions, each with five possible answers as seen in Figure~\ref{TestingFigure}.
 They were told that the test represented the breadth of topics covered by the tutor's database, and the questions were chosen randomly from a set of 5,000 possible questions.
@@
 \section{Results}
-From our study design, we define the following four conditions:\\
-\begin{enumerate}
-    \item{PUBPP} Subject used public computer, and pen \& paper for evaluation.
-    \item{PUBCE} Subject used public computer and computer for evaluation.
-    \item{PCPP} Subject used personal computer and pen \& paper for evaluation.
-    \item{PCCE} Subject used personal computer and computer for evaluation.
-\end{enumerate}
 
-We considered further aggregate conditions such as personal (PCPP and PCCE), public (PUBPP and PUBCE) based on which computer type was used by the subject for the study, and pen \& paper, computer based on which medium was used by the subject to evaluate the computer and human researchers.
-Figure \ref{fig:fourCondAvg} shows the average scores for computer evaluations by each of the nine questions across all four conditions.
-When considering the aggregate groups, figure \ref{fig:pervpub} and \ref{fig:ppvcomp} displays the average scores for computer evaluations by question for personal vs public and computer vs pen \& paper respectively.
+In the original Nass et al.
+study, the researchers observed significant interviewer bias.
+In their results, the difference between the raw mean scores of same computer and paper-pencil evaluation was 1.1 \cite{nass1999people}.
+The researchers relied upon heterogeneity of the evaluation scores to determine this bias, where heterogeneity refers to the degree of the evaluation scores being non-uniform.
+To measure heterogeneity of the scores, Nass and colleagues used standard deviation and both same computer and paper-pencil displayed a standard deviation of 0.44.
+
+In contrast, the four conditions in our study did not display any such significant results, as can be seen in the average score by question for all four conditions in figure \ref{fig:fourCondAvg}.
+This graph also implies that there were no significant difference between the two independent variables in our study - the computer condition (public vs personal) and the evaluation condition (computer vs pen and paper).
+This is further reinstated by the analysis of variance (ANOVA) results in table \ref{table:anova} across the two evaluation criteria - the computer tutor and the human researchers.
 
@@
 
-\begin{figure}[h]
-\includegraphics[width=\columnwidth]{ScorebyQuestion_persVpub}
-\centering
-\caption{Average computer scores by question : personal vs public computers}
-\label{fig:pervpub}
-\end{figure}
+\begin{table}[h]
+\resizebox{\columnwidth}{!}{\begin{tabular}{|c|c|}
+\hline
+Condition    & P-Value\\
+\hline
+Programmer Experience (Computer) & 0.1 $\cdot$\\
+Programmer Experience (Human) & 0.62\\
+Type (Human) &  0.65\\ 
+Type (Computer) & 0.38\\
+\hline
+\end{tabular}}
+\caption{Analysis of Variance Results}
+\label{table:anova}
+\end{table}
 
-\begin{figure}[h]
-\includegraphics[width=\columnwidth]{ScorebyQuestion_ppVcomp}
-\centering
-\caption{Average computer scores by question : pen and paper vs computer}
-\label{fig:ppvcomp}
-\end{figure}
+The independent variables under investigation in our study - the computer condition (public vs personal) and the evaluation condition (computer vs pen and paper), each embodies our research questions individually, and with our results we answer them here separately.\\
 
-To get a better idea of the distribution of the computer evaluation scores over the conditions, figure \ref{fig:compBoxPlot} and \ref{fig:humanBoxPlot} show the box and whisker plots for the computer and human researcher evaluation scores respectively.
+\textit{RQ1: Do software developers exhibit the social bias phenomena identified in previous studies?}\\
+Our results do not indicate any existence of the social bias observed by the prior studies.
+Using standard deviation (SD) as a measure of homogeneity with a cut-off of $SD=0.44$ and the human researcher scoring as control, we identified 10 samples from our study population of 26 to be homogeneous.
+We also conducted two-sample t-tests between the evaluation scores of human researchers and the computer, both including and excluding the homogeneous samples.
+These results are displayed in table \ref{table:ttest}.
+There are significant differences between the two evaluations - both including the homogeneous samples ($p=2.01*10^{-6}, \alpha=0.001$) and excluding the homogeneous samples ($p=0.005, \alpha=0.01$).
 
-\begin{figure}[h]
+\begin{figure}[h!]
 \includegraphics[width=\columnwidth]{compBoxPlot}
@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
 \includegraphics[width=\columnwidth]{humanBoxPlot}
@@
 \end{figure}
-
-To answer our research questions, we conducted two tailed T-tests over 9 different measurements in our data, here displayed in table \ref{table:ttest}. With these
 
@@
 
-\begin{table}[h]
-\resizebox{\columnwidth}{!}{\begin{tabular}{|c|c|}
-\hline
-Condition    & P-Value\\
-\hline
-Programmer Experience (Computer) & 0.62\\
-Programmer Experience (Human) & 0.1 $\cdot$\\
-Type (Human) &  0.65\\ 
-Type (Computer) & 0.38\\
-\hline
-\end{tabular}}
-\caption{Analysis of Variance Results}
-\label{my-label}
-\end{table}
+This is further evident in the distribution of computer and human researcher evaluation scores over all four conditions in figure \ref{fig:compBoxPlot} and figure \ref{fig:humanBoxPlot} respectively.
+This clearly indicates the absence of the politeness bias observed in the previous studies.
+Furthermore, we used linear regression to determine if there is any correlation between programmer experience and the evaluation scores.
+Our p-value for correlation between programmer experience and human researcher evaluations result is 0.616, which is well above any acceptable $\alpha$.
+However, for correlation between programmer experience and human researcher evaluations the p-value of the result is 0.09998, which can be considered significant with an $\alpha$ of 0.01, but for the sake of consistency this paper assumes $\alpha$ to be 0.001 and hence we rule out any such correlation.\\
+
+\textit{RQ2: Does a software developer's familiarity with a computing environment affect the social bias phenomena?}\\
+Again our results do not display any existence of significance of software developer's familiarity with a computing environment on the evaluation scores.
+We conducted two-sample t-tests over the measurements of computer and human researcher evaluation scores over public computer and personal computer.
+From table \ref{table:ttest}, we can see that there is no significant difference between these scoring with a p-value of 0.2982 and 0.95 for computer and human researcher evaluations respectively ($\alpha=0.05$).
+Comparing the t-test results of computer and human researcher evaluation scores over both the evaluation mediums - computer and pen \& paper, we again fail to establish any significant difference.
+Based on our results, we can safely rule out the effect of a software developer's familiarity with a computer on the social bias observed in the previous studies.
+
+\subsection{Additional Results}
+To determine the effect of selection bias that we may have encountered during the study between the classroom on day 1, and the students who elected to participate in the study on day 2, we conducted two further t-tests: human researcher evaluation scores on day 1 vs day 2 and computer evaluation scores on day 1 and day 2.
+
+In table \ref{table:ttest}, we can see that there is a significant difference in means between the human scores from day 1 vs day 2 with a p-value of 0.009 ($\alpha=0.01$), but the difference in means which we can see between the two measurements is very small, 0.65 ($\mu_{Day 1}=9.11$ vs $\mu_{Day 2}=9.76$).
+However, we do not find a significant difference between the computer scoring on the two days as seen in table \ref{table:ttest} with a high p-value of 0.9046 ($\alpha=0.01$) and the very small difference of 0.07 in scoring between the two days ($\mu_{Day 1}=7.64$ vs $\mu_{Day 2}=7.57$).
+
+To count for any potential impact of the homogeneous scorers on the human scores mentioned previously, we conducted an additional t-test of the heterogeneous scores on day 1 vs day 2 for human researcher evaluation scores.
+As seen in table \ref{table:ttest}, even excluding the homogeneous scorers, we can observe significant difference between scores on day 1 and day 2 with a p-value of 0.002 ($\alpha=0.01$) and a difference of mean of 0.92 ($\mu_{Day 1}=8.6$ vs $\mu_{Day 2}=9.52$).
 
 \section{Discussion}
+\begin{comment}
+Significant results for day one vs Day 2
+    Reasons why we might have seen this result
+\end{comment}
+The participants rated the researchers significantly higher on the second day of testing than the first day.
+However, their computer evaluation scores were not significantly different.
+There are two probable factors that can explain this effect.
+First, self-selection is a plausible  explanation since participants took time out of their schedule to run an experiment.
+However, environmental changes may also explain these results.
+Since the class all completed the experiment simultaneously, the researchers were speaking to groups of participants while giving the instructions and debriefing.
+On the second day, all interactions were one-on-one.
+Even though the researchers followed a script, the more personal experience could have effected the researcher evaluation scores.
+The second explanation is more likely when combined with the fact that the tutor's evaluation scores were statistically equivalent between the two days.
 
-\begin{itemize}
-    \item Overall discussion of the importance or lack of importance of our analysis and results.
-\end{itemize}
+\begin{comment}
+Non Significant results: Social biases towards computers were not observed in software developers
+    -> We saw one weak effect between programming experience and computer evaluation results, but more testing is needed.
+\end{comment}
+From our results, we did not observe any social biases towards computers among software developers.
+Our results cancel out any existence of the interviewer based social bias and the effect of familiarity of a computer on this bias.
+We did find a nearly considerable relationship between programming experience and computer evaluation results, but more testing is needed to be conclusive.
 
+\begin{comment}
+Why did we see these results?
+    - Software developers know more about the inner workings of computers.  Consider AI as example.
+\end{comment}
+More research is necessary to determine exactly why software developers do not exhibit the same social biases towards computers as non-software developers.
+We speculate that it has to do with software developers intricate knowledge of how software handles data.
+Artificial Intelligence is an obvious example of how developers think differently about a piece of software.
+For laymen, the computer may appear to be making decisions, and users are more likely to project a sense of "being" onto the machine.
+Software developers know that all artificial intelligence is created from well-tailored computer algorithms that manipulate data, regardless of if they know which algorithms are being employed.
+A similar effect could explain why laymen appear to exhibit politeness during computer-based interviews.
+
+\begin{comment}
+Why does it matter?
+    Surveys are a common method of evaluation.  Surveys deployed to different demographics can be informed by these results. 
+\end{comment}
+These results can and should inform how surveys are evaluated in software engineering.
+Surveys are commonly used for software assessment purposes, but developers are rarely aware of biases inherent in computer-based evaluations.
+Surveys deployed to developers should be evaluated differently than surveys deployed to laymen.
 \subsection{Threats}
